\documentclass[12pt,title,fleqn]{article}
\usepackage{url}
\usepackage{amssymb,rotating}
\usepackage{amsmath}
\usepackage{amsmath,amsfonts,amssymb,graphicx}
\usepackage{setspace,multicol}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=blue,
	citecolor=blue,
}
\usepackage{longtable} 
\usepackage{caption}
\usepackage{dcolumn}
\usepackage{array}
\usepackage[margin=1in]{geometry}
\usepackage{apacite}
\usepackage{listings}
\usepackage[margin=1in]{geometry}
\usepackage{longtable} 
\usepackage{enumitem}
\usepackage{xltabular} 
\usepackage{tabularx} 
\renewcommand{\contentsname}{Table of Contents}
\begin{document}

\begin{titlepage}
\centering
\vspace*{2cm} % Adjust vertical space as needed

{\Huge\textbf{Global Factor Data Documentation}\\[1.5cm]} % Title with increased space after

{\Large Theis Ingerslev Jensen}\\[0.5cm] 
{\Large Bryan Kelly}\\[0.5cm] 
{\Large Lasse Heje Pedersen*}\\[2cm] 

\vfill % Pushes the following content to the bottom

\vspace{1cm} % Space before the date

% Add any additional content or information here
\renewcommand{\thefootnote}{\ensuremath{\ast}}
\footnotetext{%
Jensen is at Yale School of Management; \url{www.tijensen.com}. Kelly is at AQR Capital Management, Yale School of Management, and NBER; \url{www.bryankellyacademic.org}. Pedersen is at AQR Capital Management, Copenhagen Business School, and CEPR; \url{www.lhpedersen.com}. We are grateful to Faheem Almas, Fernando Reyes De La Luz and Tyler Gwinn for excellent research assistance.  AQR Capital Management is a global investment management firm, which may or may not apply similar investment techniques or methods of analysis as described herein. The views expressed here are those of the authors and not necessarily those of AQR.}
\end{titlepage}





\tableofcontents
\newpage


\section{Overview}
    \begin{itemize}
    \item This documentation describes the Global Factor Data, and the associated code for constructing the data, based on  \cite{JensenKellyPedersen2023}.  The citation for use of this data and code is:
	\begin{verbatim}
@article{JensenKellyPedersen2023,
	author = {Jensen, Theis Ingerslev and Kelly, Bryan and Pedersen, Lasse Heje},
	title = {Is There a Replication Crisis in Finance?},
	journal = {The Journal of Finance},
	volume = {78},
	number = {5},
	pages = {2465-2518},
	year = {2023}
}	
	\end{verbatim}
	\item The Global Factor Data includes 406 characteristics and their associated factor portfolios.  This is a superset of the 153 factors analyzed in Jensen, Kelly, and Pedersen (2023).
        \item This documentation is grouped into sections covering data downloads, identifier variables, industry identifiers, helper functions, accounting characteristics, market-based characteristics, detailed characteristic construction, FX conversion rate construction, and factor details and citations.
            \begin{itemize}
                \item Data downloads describe the files available on jkpfactors.com/factor-returns and their columns.
                \item Identifier Variables include firm identifying information, date, etc...
                \item Each of the Characteristics sections includes at least three subsections: Datasets, Variables, and Characteristics.
                \item Datasets refers to which datasets the items in variables are drawn from. For example, 'COMP.FUNDA' suggests we use variables from the FUNDA dataset provided by Compustat. 
                \item Variables refers to a table containing information about the variables drawn from the datasets previously identified. These tables include the name, abbreviation used throughout the section, and the construction of the variables. These variables are constructed in a way to maximize coverage and are not directly included in the final dataset. 
                \item Characteristics refers to a table of constructed characteristics made of the previously describes variables. These tables include the name, the abbreviation used in the published dataset, and the construction. These characteristics are in the final dataset. 
            \end{itemize}
    \end{itemize}


\subsection{How To Run the Code}
    \begin{itemize}
    \item Access the code for this data set at \url{https://github.com/bkelly-lab/ReplicationCrisis}.
    \item This data is produced using the SAS Studio on Wharton Research Data Services (WRDS) servers. The github README file contains instruction on how to generate the data.
    \item Use the 'EOM' (end of month) variable as the date variable to join/merge datasets.
\end{itemize}

\subsection{How To Use the Data}
\begin{itemize}
	\item The \texttt{id} column is the unique security $\times$ source\footnote{CRSP or Compustat.} identifier.
	\item The \texttt{eom} column shows the end of month, where the data is valid. In other words, it shows the information available by the end of a given month. As an example, the \texttt{me} value for a stocks with \texttt{eom=20191231}, will be the last available market equity before or at December 31st 2019. Therefore, when predicting the return column \texttt{ret}, characteristics should be lagged by one month (as \texttt{ret} shows the return in the current month identified by \texttt{eom}). Alternatively, you can predict next month’s returns, stored in \texttt{ret\_exc\_lead1m}, without lagging the characteristics.
	\item The \texttt{excntry} column, identifies the country of the exchange where the security is traded.
	\item Suggested screens:
	\begin{itemize}
		\item To restrict the sample to one observation per security $\times$ month, use \texttt{obs\_main=1}.
		\item To restrict the sample to common stocks, use \texttt{common=1}.
		\item To restrict the sample to prominent exchanges, use \texttt{exch\_main=1}.
		\item To restrict the sample to primary listing $\times$ month, use \texttt{primary\_sec=1}.
	\end{itemize}  
	
\end{itemize}

\subsection{Versions, Bug Fixes, and Comments}
    \begin{itemize}
    \item We will update the code and data regularly as CRSP and Compustat updates become available.  We will also release periodic updates with bug fixes. Our GitHub repository: \url{https://github.com/bkelly-lab/ReplicationCrisis/blob/master/GlobalFactors/CHANGELOG.md} tracks the evolution in the code used to generate the data. Furthermore, Table \ref{Log of changes} gives an overview of the most important changes.
    \item The code and data has been carefully vetted, but may contain bugs and certainly has room for improvement.  We welcome any and all feedback regarding bugs or suggestions for improvements and extensions.
    \item Send correspondence to \href{mailto:bryan.kelly@yale.edu}{bryan.kelly@yale.edu} with subject ``Global Factor Data''
    \end{itemize}

% Log of changes

\begin{xltabular}{\textwidth}{|p{2.5cm}|X|}
\caption{Log of Important Code and Methodology\label{Log of changes}}\\
\hline
\textbf{Date} & \textbf{Changes} \\
\hline
\endfirsthead
\hline
\textbf{Date} & \textbf{Changes} \\
\hline
\endhead
03-05-2025 & 
\begin{itemize}[nosep, leftmargin=*]
    \item Updated market returns macro to add a capped value option.
    \item Corrected error in o-score calculation
\end{itemize} \\
\hline
03-03-2023 & 
\begin{itemize}[nosep, leftmargin=*]
    \item Added 'me' (market equity) and 'ret' (total return) and removed 'source\_crsp' from daily return files.
\end{itemize} \\
\hline
02-08-2022 & 
\begin{itemize}[nosep, leftmargin=*]
    \item Fixed error in the construction of intrinsic\_value. Previously, we failed to scale intrinsic\_value by market equity as done in Frankel and Lee (1998). We call the new characteristic ival\_me and keep intrinsic\_value in the data set. The alpha of the new factor based on ival\_me is significantly different from zero, while the factor based on intrinsic\_value is insignificant.
\end{itemize} \\
\hline
11-16-2021 & 
\begin{itemize}[nosep, leftmargin=*]
    \item Changed return cutoffs to depend on all stocks, instead of only stocks from CRSP.
    \item Changed the 'source' (character) column to 'source\_crsp' (integer), source\_crsp is 1 if CRSP is the return data source.
    \item Changed the 'id' column from character to integer. For stocks from CRSP, the id is just their permno. For stocks from Compustat, the first digit is 1 if the stock is traded on a US exchange, 2 if it's traded on a Canadian exchange, and 3 otherwise. The next two digits are the IID from Compustat, and the remaining six digits are the gvkey.
    \item Adapted the primary\_sec column such that all observations from CRSP have primary\_sec=1.
    \item Changed the treatment of zero return. Previously, we treated a zero return as a missing observation. Now, we have removed this screen, such that a zero return is treated like any other return.
    \item Changed the creation of characteristics based on daily stock market data. Previously, we winsorized daily returns, market equity, and dollar volume, before creating characteristics based on daily stock market data. Now, we have removed this winsorization, and daily characteristics are based on the raw data.
    \item Added the option to create daily factor return in the portfolios.R code.
    \item Added the option to create industry returns in the portfolios.R code.
\end{itemize} \\
\hline
08-27-2021 & 
\begin{itemize}[nosep, leftmargin=*]
    \item Fixed a bug regarding how daily delisting returns from CRSP are incorporated.
    \item Added indfmt='FS' to the international accounting data.
\end{itemize} \\
\hline
06-14-2021 & 
\begin{itemize}[nosep, leftmargin=*]
    \item We changed the winsorization scheme. First, we removed the 0.01\%/99.9\% winsorization of market equity in all countries. Second, we removed the winsorization of returns from the CRSP database. For Compustat returns, we set returns above (below) the 99.9\% (0.01\%) of CRSP returns in the same month, to that level. In other words, we base our winsorization of Compustat data on CRSP data from the same month.
\end{itemize} \\
\hline
02-19-2021 & 
\begin{itemize}[nosep, leftmargin=*]
    \item Previously we did not exclude securities that are only traded over the counter. In the new version of the data set, we include an indicator column "exch\_main" to exclude non-standard exchanges. In the US, the main exchanges are AMEX, NASDAQ, and NYSE. Outside of the US, we exclude over the counter exchanges, stock connect exchanges in China, and cross-country exchanges such as BATS Chi-X Europe. The documentation includes a full list of the excluded exchanges.
    \item Included SIC, NAICS, and GICS industry codes.
\end{itemize} \\
\hline
02-15-2021 & 
\begin{itemize}[nosep, leftmargin=*]
    \item Removed a bug that caused ivol\_ff3\_21d, iskew\_ff3\_21d, ivol\_hxz4\_21d, and iskew\_hxz4\_21d to require 17 (ff3) and 18 (hxz) observations for a valid estimate. Consistent with our original intent, we now require at least 15 observations for a valid estimate.
\end{itemize} \\
\hline
02-01-2021 & 
\begin{itemize}[nosep, leftmargin=*]
    \item Fixed a small bug in the bidask\_hl() macro.
    \item Lowered the requirement for the number of stocks needed when creating asset pricing factors (FF and HXZ). We previously required at least 5 stocks in a sub-portfolio (e.g., small stocks with high BM) for the observation to be valid. This led to missing observations in the 1950s for small stocks with low BM. We lowered this requirement to 3 stocks. Furthermore, when creating asset pricing factors, we changed the breakpoints to be based on NYSE stocks in the US instead of non-microcap stocks. Outside of the US, breakpoints are still based on non-microcap stocks.
\end{itemize} \\
\hline
01-25-2021 & 
\begin{itemize}[nosep, leftmargin=*]
    \item Changed residual momentum characteristics (resff3\_12\_1 \& resff3\_6\_1) to be scaled with the standard deviation of residuals consistent with Blitz, Huij, and Mertens (2011).
    \item Fixed error in creating qmj\_prof. The issue was that the oaccruals\_at used the value instead of the z-score of ranks. This effectively meant that accruals didn't impact the profitability score.
    \item Fixed error for annual seasonality characteristics (factor names starting with seas\_ and ending with \_an). There was a bug in the screening procedure which meant that the characteristic for one stock could use information from an unrelated stock.
    \item Rounding issues when converting a .csv file to an excel file, caused the zero\_trades\_* variables to not have any decimals which made the turnover tie-breaker ineffective.
    \item Standardized unexpected earnings (niq\_su) and sales (saleq\_su) is computed as the actual value minus the expected value (standardized by the standard deviation of this change). Before, the expected value was computed as the mean yearly change over the last 8 quarters added to the last quarterly value. Now the expected value is the same mean yearly change, but added to the quarterly value 4 quarters ago consistent with Jegadeesh and Livnat (2006).
\end{itemize} \\
\hline
\end{xltabular}


\subsection{Terminology}
\begin{itemize}
	\item \textit{Annual data} refers to accounting data from annual reports sourced from COMP.FUNDA and COMP.G\_FUNDA.
	
	\item \textit{Quarterly data} refers to accounting data from quarterly reports sourced from COMP.FUNDQ and COMP.G\_FUNDQ.
	
	\item \textit{Final Dataset} refers to ``world\_data.sas7bdat", the output dataset
	
	\item \textit{Fiscal period} refers to the relevant period over which income and expenses have accrued. 
	
	\item \textit{Accounting variables} refers to accounting items such as assets, sales and net income. 
	
	\item \textit{Market variables} refers to market based items such as market equity and excess return.
	
	\item \textit{Characteristics} refers to columns in the final dataset that reveals a characteristic about the security, For example asset growth, book to market equity, and net income to book equity. 
\end{itemize}


\section{Factor Portfolio Construction}
\begin{itemize}
	\item For each characteristic, we build the 1-month holding period factor return within each country as follows.  
	\item In each country and month, we sort stocks  into characteristic terciles (top/middle/bottom third)\ with breakpoints based on non-micro stocks in that country.  Specifically, we start with all non-micro stocks in a country (i.e., larger than NYSE  20$^\text{th}$ percentile) and sort them into three groups of equal numbers of stocks based on the characteristic, say book-to-market. Then we distribute the micro-cap stocks into the three groups based on the same characteristic breakpoints. This process ensures that the non-micro stocks are distributed equally among across portfolios, creating more tradable portfolios.  
	\item For each tercile, we compute its ``capped value weight'' return, meaning that we weight stocks by their market equity, winsorized at the NYSE 80$^\text{th}$ percentile. This construction ensures that tiny stocks have tiny weights and any one mega stock does not dominate a portfolio, seeking to create tradable, yet balanced, portfolios.  
	\item The factor is then defined as the high-tercile return minus the low-tercile  return, corresponding to the excess return of a long-short zero-net-investment strategy.  The factor is long (short) the tercile identified by the original paper to have the highest (lowest) expected return.  
	\item For a factor return to be non-missing, we require that it has at least 5 stocks in each of the long and short legs. We also require a minimum of 60 valid monthly observations for each country-specific factor for inclusion in our sample.  
	\item We update characteristics with the most recent accounting data (which could be either annual or quarterly) starting four months after the end of the fiscal period.
	\item To compute a cluster (theme) return, we first sign factors according to the original reference, then we equal-weight the returns of factors within a specific cluster. The signing convention and cluster allocation follows  \cite{JensenKellyPedersen2023} and we show it in table \ref{tbl:factor:details}.
\end{itemize}

\section{Public data not on jkpfactors.com}
We share long/short factor returns on \url{jkpfactors.com/factor-returns}, but we also share additional data, which can be accessed via \href{https://www.dropbox.com/scl/fo/zxha6i1zcjzx8a3mb2372/AN9kkos5H5UjjXUOqW3EuDs?rlkey=i3wkvrjbadft6hld863571dol&st=6sg3nmw0&dl=0}{this Dropbox link}. Below is an explanation of the most important files.

\subsection{Tercile Portfolio Returns (\texttt{pfs.csv} / \texttt{pfs\_daily.csv})}

\begin{itemize}
  \item \texttt{pfs.csv} / \texttt{pfs\_daily.csv} reports the monthly/daily equal weight, value weight, and capped value weight excess return for the high, middle, and low portfolios.
  \item For each characteristic, we construct 1-period holding-period portfolio returns within each country at a monthly (\texttt{pfs.csv}) or daily (\texttt{pfs\_daily.csv}) frequency.
\end{itemize}

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|l|m{14.2cm}|@{}}
	\caption{\texttt{pfs.csv} Data Columns \label{pfs-monthly}}\\
	
	\hline
	Name & Description \\
	\hline
	\endfirsthead
	
	\hline
	Name & Description \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
	
	excntry\rule{0pt}{10pt} & The country of the exchange where the security is traded. Expressed as an ISO \emph{country} code; \texttt{mul} indicates a multi-country exchange. \\[1ex]
	
	characteristic & Characteristic name used for the sort. \\[1ex]
	
	pf & Portfolio tercile. \\[1ex]
	
	eom & The last day of the month in which the observation is made. \\[1ex]

	n & Number of stocks in the tercile. \\[1ex]
    
	signal & Median value of the characteristic within the bucket and month. \\[1ex]

	ret\_ew & Equal weight return for the tercile in the month.\\[1ex]

	ret\_vw & Value weight return for the tercile in the month.\\[1ex]

	ret\_vw\_cap & Capped value weight return for the tercile in the month.\\[1ex]

\end{longtable}}

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|l|m{14.2cm}|@{}}
	\caption{\texttt{pfs\_daily.csv} Data Columns \label{pfs-daily}}\\
	
	\hline
	Name & Description \\
	\hline
	\endfirsthead
	
	\hline
	Name & Description \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
	
	pf\rule{0pt}{10pt} & Portfolio tercile. \\[1ex]

	date & The date on which the observation is made. \\[1ex]

	n & Number of stocks in the tercile. \\[1ex]

	excntry & The country of the exchange where the security is traded. Expressed as an ISO \emph{country} code; \texttt{mul} indicates a multi-country exchange. \\[1ex]
	
	characteristic & Characteristic name used for the sort. \\[1ex]
    
	ret\_ew & Equal weight return for the tercile on the date.\\[1ex]

	ret\_vw & Value weight return for the tercile on the date.\\[1ex]

	ret\_vw\_cap & Capped value weight return for the tercile on the date.\\[1ex]
	
\end{longtable}}


\subsection{GICS Industry Returns (\texttt{industry\_gics.csv})}
\begin{itemize}
    \item \texttt{industry\_gics.csv} reports for each country and month the monthly equal weight, value weight, and capped value weight return in each sector.
    \item For all stocks with non-missing GICS, we convert to 2-digit GICS sectors (first two characters of the code).
    \item For a sector return to be non-missing, the sector-month must contain at least the minimum number of constituents (\texttt{bp\_min\_n} = 10 in the current version).

\end{itemize}

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|l|m{14.2cm}|@{}}
	\caption{\texttt{industry\_gics.csv} Data Columns \label{industry_gics}}\\
	
	\hline
	Name & Description \\
	\hline
	\endfirsthead
	
	\hline
	Name & Description \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
	
	gics\rule{0pt}{10pt} & Firm GICS industry. We use historical data from Compustat. \\[1ex]
	
	eom & The last day of the month in which the observation is made. \\[1ex]

	n & Number of stocks in the sector that month. \\[1ex]

	ret\_ew & Equal weight return for the sector in the month.\\[1ex]

	ret\_vw & Value weight return for the sector in the month.\\[1ex]

	ret\_vw\_cap & Capped value weight return for the sector in the month.\\[1ex]

	excntry & The country of the exchange where the security is traded. Expressed as an ISO \emph{country} code; \texttt{mul} indicates a multi-country exchange. \\[1ex]

\end{longtable}}


\subsection{FF49 Industry Returns (\texttt{industry\_ff49.csv})}
\begin{itemize}
    \item \texttt{industry\_ff49.csv} reports the monthly equal weight, value weight, and capped value weight return for 49 SIC-based Fama-French industries (Fama and French, 1997) with the addition of a software industry in the U.S.
    \item For an industry to be non-missing, the industry-month must contain at least the minimum number of constituents (\texttt{bp\_min\_n} = 10 in the current version).

\end{itemize}

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|l|m{14.2cm}|@{}}
	\caption{\texttt{industry\_ff49.csv} Data Columns \label{industry_ff49}}\\
	
	\hline
	Name & Description \\
	\hline
	\endfirsthead
	
	\hline
	Name & Description \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
	
	ff49\rule{0pt}{10pt} & Classification of stocks into 49 industry groups based on SIC codes and the methodology in Fama and French (1997), with the addition of a software industry. \\[1ex]
	
	eom & The last day of the month in which the observation is made. \\[1ex]

	n & Number of stocks in the industry that month. \\[1ex]

	ret\_ew & Equal weight return for the industry in the month.\\[1ex]

	ret\_vw & Value weight return for the industry in the month.\\[1ex]

	ret\_vw\_cap & Capped value weight return for the industry in the month.\\[1ex]

	excntry & The country of the exchange where the security is traded. This file is U.S.-only data. \\[1ex]

\end{longtable}}

\subsection{Characteristics-Managed Portfolio Returns (\texttt{cmp.csv})}
\begin{itemize}
    \item \texttt{cmp.csv} reports for each country, characteristic, and month the size-neutral long-short excess returns with the corresponding weighted characteristic.
    \item For each characteristic, country, and month, we form characteristics-managed portfolios (CMP) within predefined size groups based on \hyperref[app:nyse-breakpoints]{NYSE size breakpoints}. Only observations with non-missing characteristic values and returns are included.
    \item Within each size group and month, we compute each stock's percentile rank on the characteristic, demean the rank within the group, and scale the deviation so long and short weights offset and the gross weight is normalized. These weights create a within-size long-short portfolio that isolates the characteristic from size.
    \item Using the within-group weights, we compute the group's next-month excess return and the weighted signal level.
\end{itemize}

{\scriptsize
\begin{longtable}{|p{0.22\textwidth}|p{0.68\textwidth}|}
\caption{NYSE Size Breakpoints Definitions}\label{app:nyse-breakpoints}\\
\hline
\textbf{Size group} & \textbf{NYSE market equity percentiles} \\
\hline
\endfirsthead

\hline
\textbf{Size group} & \textbf{NYSE market equity percentiles} \\
\hline
\endhead

\hline
\multicolumn{2}{r}{\textit{(table continues)}}\\
\endfoot

\hline
\endlastfoot

Mega\rule{0pt}{10pt}  & Top 20\% percentiles. \\[1ex]

Large & 80th--50th percentiles. \\[1ex]

Small & 50th--20th percentiles. \\[1ex]

Micro & 20th--1st percentiles. \\[1ex]

Nano  & Below 1st percentile. \\
\end{longtable}
\vspace{-0.4\baselineskip}
\noindent\footnotesize Notes: Percentiles \((p1,p20,p50,p80)\) are recomputed each month using NYSE common stocks (primary share/security, main class, non-missing market equity). Discrete quantiles are used (no interpolation).
}

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|l|m{14.2cm}|@{}}
	\caption{\texttt{cmp.csv} Data Columns \label{cmp}}\\
	
	\hline
	Name & Description \\
	\hline
	\endfirsthead
	
	\hline
	Name & Description \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
	
	excntry\rule{0pt}{10pt} & The country of the exchange where the security is traded. Expressed as an ISO \emph{country} code; \texttt{mul} indicates a multi-country exchange. \\[1ex]
	
	characteristic & Characteristic name used for the sort. \\[1ex]

	size\_grp & NYSE size group.\\[1ex]
    
    eom & The last day of the month in which the observation is made. \\[1ex]

    n\_stocks & Number of stocks in the size group that month. \\[1ex]

    ret\_weighted & Characteristics-managed excess return using CMP weights. \\[1ex]

\end{longtable}}

\subsection{NYSE Size Cutoffs (\texttt{nyse\_cutoffs.csv})}
\begin{itemize}
    \item \texttt{nyse\_cutoffs.csv} reports the monthly NYSE market equity (ME) breakpoints used for the micro-cap screen and capped value weights.
    \item For each month, we compute discrete percentiles of market equity across the NYSE universe: 1st, 20th, 50th, and 80th.
    \item The monthly cutoffs are derived from a universe of NYSE common stocks (primary share/security, main class) with non-missing market equity on CRSP.
    
\end{itemize}

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|l|m{14.2cm}|@{}}
	\caption{\texttt{nyse\_cutoffs.csv} Data Columns \label{nyse-cutoffs}}\\
	
	\hline
	Name & Description \\
	\hline
	\endfirsthead
	
	\hline
	Name & Description \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
    
    eom\rule{0pt}{10pt} & The last day of the month in which the observation is made. \\[1ex]

    n\_stocks & Number of eligible NYSE stocks that month. \\[1ex]

    nyse\_p1 & 1st percentile of ME (NYSE only). \\[1ex]

    nyse\_p20 & 20th percentile of ME (NYSE only). \\[1ex]
    
    nyse\_p50 & 50th percentile of ME (NYSE only). \\[1ex]

    nyse\_p80 & 80th percentile of ME (NYSE only). \\[1ex]

\end{longtable}}

\subsection{Monthly Return Cutoffs (\texttt{return\_cutoffs.csv})}
\begin{itemize}
    \item \texttt{return\_cutoffs.csv} reports the discrete monthly percentile return cutoffs for return winsorization.
    \item The cutoffs are derived from a monthly panel of common stocks (primary share/security, main class, non-missing market equity) with non-missing return on CRSP.
    \item For each month-end, we compute non-interpolated (list-based) cross-sectional percentiles, typically the 0.1\%/99.9\% and 1\%/99\% bounds, for three return measures: USD, local, and excess.
    \item The cutoffs can be joined back to the stock-level panel by period and used to clip returns to the chosen bounds. This mitigates data errors and outliers so equal-weighted/value-weighted aggregates and long-short factors are not driven by a few extreme observations.
\end{itemize}

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|l|m{14.2cm}|@{}}
	\caption{\texttt{return\_cutoffs.csv} Data Columns \label{return-cutoffs}}\\
	
	\hline
	Name & Description \\
	\hline
	\endfirsthead
	
	\hline
	Name & Description \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
    
    eom\rule{0pt}{10pt} & The last day of the month in which the observation is made. \\[1ex]

    n & Number of eligible stock-month observations. \\[1ex]

    return\_0\_1 & 0.1st percentile of USD return. \\[1ex]

    return\_1 & 1st percentile of USD return. \\[1ex]
    
    return\_99 & 99th percentile of USD return. \\[1ex]

    return\_99\_99 & 99.99th percentile of USD return. \\[1ex]

    return\_local\_0\_1 & 0.1st percentile of local return. \\[1ex]

    return\_local\_1 & 1st percentile of local return. \\[1ex]
    
    return\_local\_99 & 99th percentile of local return. \\[1ex]

    return\_local\_99\_99 & 99.99th percentile of local return. \\[1ex]

    return\_exc\_0\_1 & 0.1st percentile of excess return. \\[1ex]

    return\_exc\_1 & 1st percentile of excess return. \\[1ex]
    
    return\_exc\_99 & 99th percentile of excess return. \\[1ex]

    return\_exc\_99\_99 & 99.99th percentile of excess return. \\[1ex]

    eom\_lag1 & Previous month-end date for the observation (that is, \texttt{eom} shifted back one month). \\[1ex]

\end{longtable}}

\subsection{Daily Return Cutoffs (\texttt{return\_cutoffs\_daily.csv})}
\begin{itemize}
    \item \texttt{return\_cutoffs\_daily.csv} reports the discrete calendar-month percentile return cutoffs for return winsorization.
    \item The cutoffs are derived from a daily panel of common stocks (primary share/security, main class, non-missing market equity) with non-missing return on CRSP.
    \item For each trading day, we extract year and month, then group stocks by (year, month). Within each group, we compute non-interpolated cross-sectional percentiles, typically the 0.1\%/99.9\% and 1\%/99\% bounds, for three return measures: USD, local, and excess.
    \item The cutoffs can be joined back to the stock-level panel by period and used to clip returns to the chosen bounds. This mitigates data errors and outliers so equal-weighted/value-weighted aggregates and long-short factors are not driven by a few extreme observations.
\end{itemize}

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|l|m{14.2cm}|@{}}
	\caption{\texttt{return\_cutoffs\_daily.csv} Data Columns \label{return-cutoffs-daily}}\\
	
	\hline
	Name & Description \\
	\hline
	\endfirsthead
	
	\hline
	Name & Description \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
    
    year\rule{0pt}{10pt} & Calendar year extracted from the trading date. \\[1ex]

    month & Calendar month (1--12) extracted from the trading date. \\[1ex]

    n & Number of eligible stock-day observations in that year-month group. \\[1ex]

    return\_0\_1 & 0.1st percentile of USD return. \\[1ex]

    return\_1 & 1st percentile of USD return. \\[1ex]
    
    return\_99 & 99th percentile of USD return. \\[1ex]

    return\_99\_99 & 99.99th percentile of USD return. \\[1ex]

    return\_local\_0\_1 & 0.1st percentile of local return. \\[1ex]

    return\_local\_1 & 1st percentile of local return. \\[1ex]
    
    return\_local\_99 & 99th percentile of local return. \\[1ex]

    return\_local\_99\_99 & 99.99th percentile of local return. \\[1ex]

    return\_exc\_0\_1 & 0.1st percentile of excess return. \\[1ex]

    return\_exc\_1 & 1st percentile of excess return. \\[1ex]
    
    return\_exc\_99 & 99th percentile of excess return. \\[1ex]

    return\_exc\_99\_99 & 99.99th percentile of excess return. \\[1ex]

\end{longtable}}
    
\section{Identifier Variables}
This section covers all of the variables that give firm/date level identifiers and information. If a variable starts with 'comp' or 'crsp', then the following variable name is drawn from the specified dataset. For example, 'crsp\_shrcd' is the 'shrcd' variable from CRSP.

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|l|m{14.2cm}|@{}}
	\caption{Identifier Variables \label{identification_var}}\\
	
	
	
	\hline
	Name & Description \\
	\hline
	\endfirsthead
	
	\hline
	Name & Description \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
	
		size\_grp & This groups each firm into one of five categories: Mega, large, small, micro and nano cap. The groups are non-overlapping and the breakpoints are based on the market equity of NYSE stocks by the end of each month. In particular, Mega caps are stocks with a market cap above the 80th percentile of NYSE stocks, large caps are all remaining stocks above the 50th percentile, small caps are above the 20th percentile, micro caps above the 1st percentile and nano caps are the remaining stocks. \\[1ex]
		
		id & We generate a unique number for each security in our data set. For securities from CRSP, the id is just the corresponding \texttt{permno}. For stocks from Compustat, the first digits is 1 if the stocks is traded on a US exchange, 2 if it's traded on a Canadian exchange, and 3 otherwise. The next six digits are the  \texttt{gvkey} and the last two are the \texttt{iid}.\footnote{In Compustat, a security is identified by gvkey and iid. To map our id to Compustat, add 'C' or 'W' to the iid if the first digit is 2 or 3 respectively.}  \\[1ex]
		
		source\_crsp & Identifies the source of the return data. A 1 (0), indicates that the source is CRSP (Compustat). \\[1ex]
		
		obs\_main & For US stocks, we often have two observations for each security-month pair. One from Compustat, and one from CRSP. In cases with duplicates, the observation from CRSP has \texttt{obs\_main=1}, and the observation from Compustat has \texttt{obs\_main=0}.  
		If there are more than one firm observations for one date, this identifies if the observation is considered as the 'main' observation. If available, CRSP observations are considered as the 'main' observation.\\[1ex]
		
		exch\_main & Indicator for ordinary exchanges. If CRSP is the source, main exchanges are those with \textit{crsp\_exchcd} 1, 2 and 3. If Compustat is the source, main exchanges are all \texttt{comp\_exchg} except 0, 1, 2, 3, 4, 13, 15, 16, 17, 18, 19, 20, 21, 127, 150, 157, 229, 263, 269, 281, 283, 290, 320, 326, 341, 342, 347, 348, 349, 352.  \\[1ex]
		
		gvkey & Permanent six-digit unique firm identifier from Compustat\\[1ex]
		
		iid & Permanent two-digit addition to 'gvkey' that identifies specific security of a firm from Compustat\\[1ex]
		
		primary\_sec &  Primary security as identified by Compustat. A 'gvkey' can have up to three different primary securities ('iid)' at a given time (US, CA, and international). All observations from CRSP has \texttt{primary\_sec=1}.  \\[1ex]
		
		permco & Permanent unique firm identifier from CRSP\\[1ex]
		
		permno & Permanent security identifier from CRSP\\[1ex]
		
		excntry & The country of the exchange where the security is traded. Usually expressed as an ISO currency code with the exception of \textit{mul} which indicates a multi country exchange\footnote{Typically over the counter exchanges.}\\[1ex]
		
		curcd & Currency of \textit{prc\_local} and the currency used to calculated \textit{ret\_local}. \\[1ex]
		
		fx & Ratio of \textit{curcd} to USD at the date of observation\\[1ex]
		
		common & Indicator for common stocks. If CRSP is the source, common is one if the SHRCD variable is 10, 11 or 12. If Compustat is the source, common is one if TPCI is '0'  \\[1ex]
		
		comp\_tpci & Compustat issue type identifier \\[1ex]
		
		crsp\_shrcd & CRSP share code\\[1ex]
		
		comp\_exchg & Compustat stock exchange code \\[1ex]
		
		crsp\_exchd & CRSP stock exchange code \\[1ex]
		
		date & Date of the last return observation during the month. \\[1ex]
		
		eom & The last day of the month in which the observation is made\\[1ex]
		
		adjfct & Share adjustment factor, using 'cfacshr' if the source is CRSP or 'ajexdi' if the source is Compustat \\
	
\end{longtable}
}

\section{Industry Identification}
    This section describes the industry identifiers. First we contruct separate identifiers for CRSP and Compustat. Based on these datasets, we create one SIC, NAICS and GICS code for each firm based on Compustat data if available and otherwise CRSP. GVKEY is the company identifier for COMPUSTAT. PERMNO is the security identifier for CRSP. While we would prefer to use PERMCO, which is company level, different firms with different industry identifications can be listed under the same PERMCO. CRSP identifiers are available on a daily basis. For Compustat, we extract SIC and NAICS codes from annual accounting reports. Historical GICS codes are only available in Compustat. The Fama-French industry identifier is mapped from SIC codes using documentation provided by Ken French. We provide classifications at eight levels of granularity (5, 10, 12, 17, 30, 38, 48, and 49 industries), as defined on \href{https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html}{Ken French's data library}.

\subsection{Datasets}
\begin{itemize}
    \item CRSP.DSENAMES
    \item COMP.FUNDA
    \item COMP.G\_FUNDA
    \item COMP.CO\_HGIC
    \item COMP.G\_CO\_HGIC
\end{itemize}

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|l|m{14.2cm}|@{}}
	\caption{Identifier Variables \label{identification_var}}\\
	
	\hline
	Name & Description \\
	\hline
	\endfirsthead
	
	\hline
	Name & Description \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
	
	sic & Firm SIC industry. We use Compustat data if available and otherwise use CRSP data. \\[1ex]
	
	naics & Firm NAICS industry. We use Compustat data if available and otherwise use CRSP data. \\[1ex]
	
	gics & Firm GICS industry. We use historical data from Compustat. \\[1ex]
	
	ff\textit{z} & Fama-French industry classification based on SIC codes \citeA{frenchdata}, where \textit{z} $\in \{5, 10, 12, 17, 30, 38, 48, 49\}$ denotes the number of industry groups. \\[1ex]

\end{longtable}}


\section{Helper Functions}

This section describes functions that we use to create variables. Many of the functions are used for variables with quarterly, monthly and daily frequencies, and these are specified by ``\_zQ", ``\_zM" and ``\_zD" respectively, where ``z" is the number of quarters, months or days that the function is referencing. For example, COVAR\_12M(X, Y) is the covariance of variables X and Y over the past 12 months.

{\scriptsize
\renewcommand{\arraystretch}{2}
	\begin{longtable}{@{\extracolsep{\fill}}|m{5cm}|l|m{8cm}|@{}}		\caption{Helper Functions \label{helper_func}}\\
		
		\hline
		Function & Name & Description \\
		\hline
		\endfirsthead
		
		\hline
		Function & Name & Description \\
		\hline
		\endhead
		
		\hline
		\endfoot
		
		\hline\hline
		\endlastfoot
		
		Mean & $\overline{X}_z$& $\frac{1}{z}\sum_{n = 0}^{z-1} X_{t-n}$\\
		
		Variance & VARC\_z(X) &  $\frac{1}{z-1}\sum_{n = 0}^{z-1} (X_{t - n} - \overline{X_t}_z)^2$\\
		
		Covariance & COVAR\_z(X, Y) & $\frac{1}{z-1}\sum_{n = 0}^{z-1} (X_{t - n} - \overline{X_t}_z)(Y_{t - n} - \overline{Y_t}_z)$\\
		
		Standard Deviation & $\sigma_z(X)$ &$\sqrt{VARC\_z(X)}$\\
		
		Skewness & SKEW\_z(X) &$\frac{1}{z\times \sigma_z(X)^3}\sum_{n = 0}^{z-1} (X_{t - n} - \overline{X_t}_z)^3$\\
		
		Standardized Unexpected Realization & SUR\_z(X) & $\frac{X_t - (X_{t - 3} + \overline{(X_{t - 3} - X_{t - 15})}_z / 4)}{\sigma_z(X_{t - 3} - X_{t - 15})}$\\
		
		Change to Expectations & CHG\_TO\_EXP(X) &$\frac{X_t}{(X_{t-12} + X_{t-24})/2}$ \\
		
		Maximum & MAXn\_z(X) &
		The maximum n values of given input. \\
		
		\hline
		\multicolumn{3}{|c|}{Quality Minus Junk Helpers} \\
		\hline
		
		Earnings Volatility & $\_EVOL$ & $ROEQ\_BE\_STD \times 2$. If this is unavailable, we use $ROE\_BE\_STD$. \\
		
		Rank of Variable & $\_rVar$ & Cross-sectional rank of Var within a country\footnote{$OACCRUALS\_AT$, $BETABAB\_1260d$, $DEBT\_AT$ and $\_EVOL$ are sorted in descending order. All other variables are sorted in ascending order.} \\
		
		Z transformation & $ZV(rVar)$ & $\frac{\_rVAR - \overline{\_rVAR}_z}{\_t(\_rVAR)}$
	\end{longtable}
}

\section{Accounting Characteristics}
\subsection{Datasets}
\begin{itemize}
	\item COMP.FUNDA
	\item COMP.FUNDQ
	\item COMP.G\_FUNDA
	\item COMP.G\_FUNDQ
\end{itemize}



\subsection{General Information}
\begin{itemize}
	\item  We create characteristics for annual and quarterly accounting data separately. We then take the most recent characteristics value from each dataset to create the final dataset. 
	
	\item We assume that accounting variables are publically available 4 months after the end of the accounting period.  
	
	\item In describing accounting variables, we use the Compustat item names from the annual dataset. The equivalent item name in the quarterly dataset can be found by adding a ‘q’ or ‘y’ to the end of the annual item name. Specifically, ‘q’ indicates a value calculated over one quarter while ‘y’ refers to the cummulative value over the quarters with data available within a fiscal year.  
\end{itemize}

\subsection{Annualized Accounting Variables from Quarterly Data}
\begin{itemize}
	\item The value of a balance sheet item such as asset or book equity has the same meaning in the annual and the quarterly data. It is the value by the end of a fiscal period. 
	
	\item The value of an income or cash flow statement item is different. In the annual data, it is calculated over one year. However, in the quarterly data, it is calculated over one quarter. To make quarterly income and cash flows items comparable to the corresponding annual item, we take the sum of the item over the last four quarters. 
\end{itemize}

\subsection{Accounting Variables}
The abbreviation is used to refer to the accounting variable. A suffix of '\mbox{*}' indicates that we have altered the original Compustat item to increase the coverage or to create a variable that is a part of creating a characteristic in the final dataset. The characteristic name will reflect the accounting name except the '\mbox{*}' suffix. As an example, 'gp\_at' is gross profit scaled by assets. In general, we will refer to Compustat variables using capital letters.   

\setlength\LTcapwidth{\textwidth} % default: 4in (rather less than \textwidth...)      

\setlength\LTleft{0pt}            % default: \fill
\setlength\LTright{0pt}           % default: \fill    

%\begin{longtable}[l]{| p{4cm} | p{2cm} | p{11cm} | }
{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|m{5cm}|l|m{8cm}|@{}}
		\caption{Accounting Variables \label{accounting_var}}\\
	
	
	\hline
	Name & Abbreviation & Construction \\
	\hline
	\endfirsthead
	
	\hline
	Name & Abbreviation & Construction \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	
	\hline\hline
	\endlastfoot
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Income Statement}} \\
	\hline 
	
	Sales & sale\mbox{*} & We prefer \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/SALE/}{SALE}. If this is unavailable, we use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/REVT/}{REVT}    \\
	
	Cost of Goods Sold & cogs & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/COGS/}{COGS}\\
	
	Gross Profit & gp\mbox{*} & We prefer to use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/GP/}{GP}. If this is unavailable we use sale\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/COGS/}{COGS} \\
	
	Selling, General and Administrative Expenses & xsga  & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XSGA/}{XSGA}\\
	
	Advertising Expenses & xad & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XAD/}{XAD}. Note that this is not available in Compustat Global\\
	
	Research and Development Expenses & xrd & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XRD/}{XRD}. Note that this is not available in Compustat Global \\ 
	
	Staff Expenses & xlr & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XLR/}{XLR}\\
	
	Special Items & spi & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/SPI/}{SPI}\\
	
	Operating Expenses & opex\mbox{*} & We prefer to use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XOPR/}{XOPR}. If this is unavailable, we use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/COGS/}{COGS}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XSGA/}{XSGA}\\
	
	Operating Income Before Depreciation &  ebitda\mbox{*} & We prefer to use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/EBITDA/}{EBITDA}. If this is unavailable, we use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/OIBDP/}{OIBDP}. If this is unavailable, we use SALE\mbox{*}-OPEX\mbox{*}. If this is unavailable, we use GP\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XSGA/}{XSGA}\\
	
	Depreciation and Amortization &  dp & Compustat Item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/DP/}{DP}\\
	
	Operating Income After Depreciation & ebit\mbox{*} & We prefer to use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/EBIT/}{EBIT}. If this is unavailable, we use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/OIADP/}{OIADP}. If this is unavailable, we use EBITDA\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/DP/}{DP}\\
	
	Interest Expenses &  int & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XINT/}{XINT} \\
	
	Operating Profit ala Ball et al (2015) & op\mbox{*} & We use EBITDA\mbox{*} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XRD/}{XRD}. If XRD is unavailable, we set it to zero \\
	
	Operating Profit to Equity & ope\mbox{*} & We use EBITDA\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XINT/}{XINT}. Note that we target the same variable as the numerator of the profitability characteristic used to create the Robust-minus weak factor in the fama-French 5 factor model (Fama and French, 2015) \\
	
	Earnings before Tax and Extraordinary Items & pi\mbox{*} & We prefer to use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/PI/}{PI}. If this is unavailable we use EBIT\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XINT/}{XINT}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/SPI/}{SPI}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/NOPI/}{NOPI} where we set SPI and NOPI to zero if missing\\
	
	Income Tax & tax & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/TXT/}{TXT}\\
	
	Extraordinary Items and Discontinued Operations &  xido\mbox{*} & We prefer to use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XIDO/}{XIDO}. If this is unavailable, we use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XI/}{XI}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/DO/}{DO} where we set DO to zero if missing. The reason why we set missing DO to zero is because it is not available in COMP.G\_FUNDQ \\
	
	Net Income & ni\mbox{*} & We prefer to use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/IB/}{IB}. If this is unavailable, we use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/NI/}{NI}-XIDO\mbox{*}. If this is unavailable, we prefer PI\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/TXT/}{TXT}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/MII/}{MII}. If MII is unavailble, it is set to zero\\
	
	Net Income Including Extraordinary Items & nix\mbox{*} & We prefer 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/NI/}{NI}. If this is not available, we prefer NI\mbox{*}+XIDO\mbox{*}. If XIDO\mbox{*} is unavailable, we set it to zero. If that is unavailable, we prefer NI\mbox{*}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XI/}{XI}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/DO/}{DO} \\
	
	Firm Income  & fi\mbox{*} & We use NIX\mbox{*}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XINT/}{XINT} \\
	
	Dividends for Common Shareholds & dvc & Compustat Item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/DVC/}{DVC}\\
	
	Total Dividends & div\mbox{*} & We prefer  \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/DVT/}{DVT}. If this is not available, we use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/DV/}{DV} \\
	
	Income Before Extraordinary Items & ni\_qtr\mbox{*} & We use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/IB/}{IBQ} \\
	
	Net Sales & sale\_qtr\mbox{*} & We use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/SALE/}{SALEQ} \\
		
	\hline 
	\multicolumn{3}{|c|}{\textbf{Cash Flow Statement}} \\
	\hline 

	Capital Expenditures  & capx & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/CAPX/}{CAPX} \\
	
	Capital Expenditures to Sales & capex\_sale\mbox{*} &
	We use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/CAPX/}{CAPX} / SALE\mbox{*} \\
	
	%Operating Cash Flow & ocf & We prefer to use \href{https://wrds-web.wharton.upenn.edu/wrds/support/Data/_001Manuals and Overviews/_001Compustat/_001North America - Global - Bank/_000dataguide/oancf_1.cfm}{OANCF}-\href{https://wrds-web.wharton.upenn.edu/wrds/support/Data/_001Manuals and Overviews/_001Compustat/_001North America - Global - Bank/_000dataguide/xidoc_2.cfm}{XIDOC} where we set XIDOC to zero if missing. If this is not available, we infer the operating cash flow from the income and balance sheet following e.g. Nallareddy et al (2018). More specifically, we compute it as IB\mbox{*}-(yearly\_chg(\href{https://wrds-web.wharton.upenn.edu/wrds/support/Data/_001Manuals and Overviews/_001Compustat/_001North America - Global - Bank/_000dataguide/act.cfm}{ACT}-\href{https://wrds-web.wharton.upenn.edu/wrds/support/Data/_001Manuals and Overviews/_001Compustat/_001North America - Global - Bank/_000dataguide/che.cfm}{CHE})-yearly\_cng(\href{https://wrds-web.wharton.upenn.edu/wrds/support/Data/_001Manuals and Overviews/_001Compustat/_001North America - Global - Bank/_000dataguide/lct.cfm}{LCT}-\href{https://wrds-web.wharton.upenn.edu/wrds/support/Data/_001Manuals and Overviews/_001Compustat/_001North America - Global - Bank/_000dataguide/dlc.cfm}{DLC})-\href{https://wrds-web.wharton.upenn.edu/wrds/support/Data/_001Manuals and Overviews/_001Compustat/_001North America - Global - Bank/_000dataguide/dp.cfm}{DP}) where $\text{yearly\_cng}(x)=x_t-x_{t-12}$\\
	
	Free Cash Flow  & fcf\mbox{*} & We use OCF\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/CAPX/}{CAPX}. Note that the free cash flow is computed before financing activities and sale of assets is taken into account \\
	
	Equity Buyback & eqbb\mbox{*} & We use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/PRSTKC/}{PRSTKC}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_global_daily_gfunda_dataitemsmz/PURTSHR/}{PURTSHR} Equity Buyback is mainly PRSTKC in NA and PURTSHR in GLOBAL. Either of PRSTKC or PURTSHR are allowed to be missing\\
	
	Equity Issuance & eqis\mbox{*} & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/SSTK/}{SSTK}\\
	
	Equity Net Issuance & eqnetis\mbox{*} & We use EQIS\mbox{*}-EQBB\mbox{*}. Either EQIS\mbox{*} or EQBB\mbox{*} are allowed to be missing \\
	
	Net Equity Payout & eqpo\mbox{*} & We use DIV\mbox{*}+EQBB\mbox{*} \\
	
	Equity Net Payout & eqnpo\mbox{*} & We use DIV\mbox{*}-EQNETIS\mbox{*} \\
	
	Net Long-Term Debt Issuance & dltnetis\mbox{*} & We prefer to use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/DLTIS/}{DLTIS}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/DLTR/}{DLTR} where we only require that one of the items are non-missing. If this is unavailable, we use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_global_daily_gfunda_dataitemsal/LTDCH/}{LTDCH}. If this is unavailable we use the yearly change in long-term book debt \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLTT/}{DLTT} \\
	
	Net Short-Term Debt Issuance & dstnetis\mbox{*} & We prefer \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/DLCCH/}{DLCCH}. If this is unavailable, we use the yearly change in short-term book debt \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLC/}{DLC}\\
	
	Net Debt Issuance & dbnetis\mbox{*} & We use DLTNETIS\mbox{*}+DSTNETIS\mbox{*} and only require one of the items to be non-missing \\
	
	Net Issuance & netis\mbox{*} & We use EQNETIS\mbox{*}+DBNETIS\mbox{*} and require that both EQNETIS\mbox{*} and DBNETIS\mbox{*} are non-missing \\
	
	Financial Cash Flow & fincf\mbox{*} & We prefer \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/FINCF/}{FINCF}. If this is unavailable, we use NETIS\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/DV/}{DV}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/FIAO/}{FIAO}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/TXBCOF/}{TXBCOF}. If FIAO or TXBCOF is missing, it is set to zero\\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Balance Sheet - Assets}} \\
	\hline 
	
	Total Assets & at\mbox{*} & We prefer to use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/AT/}{AT}. If this is unavailable, then we use SEQ\mbox{*} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLTT/}{DLTT} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/LCT/}{LCT} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/LO/}{LO} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/TXDITC/}{TXDITC}. If LCT, LO, or TXDITC are missing, then they are set to zero \\
	
	Current Assets & ca\mbox{*} & We prefer \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/ACT/}{ACT}. If this is unavailable, we use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/RECT/}{RECT}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/INVT/}{INVT}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/CHE/}{CHE}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/ACO/}{ACO}\\
	
	Account Receivables &  rec & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/RECT/}{RECT}\\
	
	
	Cash and Short-Term Investment & cash & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/CHE/}{CHE} \\
	
	Inventory & inv & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/INVT/}{INVT}\\
	
	Non-Current Assets & nca\mbox{*} & We use AT\mbox{*} - CA\mbox{*}\\
	
	Intangible Assets & intan & Compustat item 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/INTAN/}{INTAN}\\
	
	Investment and Advances & ivao & Compustat item 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/IVAO/}{IVAO} \\
	
	Property, Plans and Equipment Gross & ppeg & Compustat item
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/PPEGT/}{PPEGT} \\
	
	Property, Plans and Equipment Net & ppen & Compustat item 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/PPENT/}{PPENT}\\

	\hline 
	\multicolumn{3}{|c|}{\textbf{Balance Sheet - Liabilities}} \\
	\hline 
		
	Total Liabilities & lt & Compustat item 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/LT/}{LT}\\
	
	Current Liabilities & cl\mbox{*} & We prefer 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/LCT/}{LCT}. If this is unavailable, we use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/AP/}{AP}+
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLC/}{DLC}+ 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/TXP/}{TXP}+ 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/LCO/}{LCO}\\
	
	Accounts Payable & ap & Compustat item 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/AP/}{AP}\\
	
	Short-Term Debt & debtst & Compustat item 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLC/}{DLC}\\
	
    Income Tax Payable & txp & Compustat item 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/TXP/}{TXP} \\
    
    Non-Current Liabilities & ncl\mbox{*} & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/LT/}{LT}-CL\mbox{*} \\
    
    Long-Term Debt & debtlt & Compustat item 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLTT/}{DLTT} \\
    
    Deferred Taxes and Investment Credit & txditc\mbox{*} & We prefer to use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/TXDITC/}{TXDITC}. If this is unavailable, we use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/TXDB/}{TXDB}+
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/ITCB/}{ITCB} \\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Balance Sheet - Financing}} \\
	\hline 
	
	Preferred Stock & pstk\mbox{*} & We prefer to use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/PSTKRV/}{PSTKRV}. If this is unavailable, we use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/PSTKL/}{PSTKL}. If this is unavilable, we use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/PSTK/}{PSTK} \\
	
	Total Debt & debt\mbox{*} & We use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLTT/}{DLTT}+
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLC/}{DLC}. Either DLTT or DLC are allowed to me missing\\
	
	Net Debt & netdebt\mbox{*} & We use DEBT\mbox{*}-
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/CHE/}{CHE} where we set CHE to zero if missing \\
	
	Shareholders Equity & seq\mbox{*} & We prefer to use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/SEQ/}{SEQ}. If this is unavailable, we use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/CEQ/}{CEQ}+PSTK\mbox{*} where we set PSTK\mbox{*} to zero if missing. If this is unavailable, we use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/AT/}{AT}-
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/LT/}{LT} \\
	
	Book Equity & be\mbox{*} & We use SEQ\mbox{*}+TXDITC\mbox{*}-PSTK\mbox{*} where we set TXDITC\mbox{*} and PSTK\mbox{*} to zero if missing \\
	
	Book Enterprise Value & bev\mbox{*} & We prefer to use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/ICAPT/}{ICAPT}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLC/}{DLC}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/CHE/}{CHE} where DLC and CHE are set to zero if missing. If this is unavailable, we use SEQ\mbox{*}+NETDEBT\mbox{*}+
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/MIB/}{MIB} where we set MIB to zero if missing. In the global data \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/ICAPT/}{ICAPT} is reduced by Treasury stock \\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Balance Sheet - Summary}} \\
	\hline 	
	
	Net Working Capital & nwc\mbox{*} & We use CA\mbox{*}-CL\mbox{*} \\

	Current Operating Assets & coa\mbox{*} & We use CA\mbox{*}-
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/CHE/}{CHE} \\
	
	Current Operating Liabilities & col\mbox{*} & We use CL\mbox{*}-
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLC/}{DLC}. If DLC is missing, it is set to zero \\
	
	Current Operating Working Capital & cowc\mbox{*} & We use COA\mbox{*}-COL\mbox{*} \\
	
	Non-Current Operating Assets & ncoa\mbox{*} & We use AT\mbox{*} - CA\mbox{*}-
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/IVAO/}{IVAO} \\
	
	Non-Current Operating Liabilities & ncol\mbox{*} & We use 
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/LT/}{LT}-CL\mbox{*}-
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/DLTT/}{DLTT} \\
	
	Net Non-Current Operating Assets & nncoa\mbox{*} & We use NCOA\mbox{*}-NCOL\mbox{*} \\
	
	Financial Assets & fna\mbox{*} & We use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/IVST/}{IVST}+
	\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/IVAO/}{IVAO}. If either is missing, they are set to zero\\
	
	Financial Liabilities & fnl\mbox{*} & We use DEBT\mbox{*}+PSTK\mbox{*}. If PSTK\mbox{*} is missing, it is set to zero \\
	
	Net Financial Assets & nfna\mbox{*} & We use FNA\mbox{*}-FNL\mbox{*} \\
	
    Operating Assets & oa\mbox{*} & We use COA\mbox{*}+NCOA\mbox{*} \\
    
    Operating Liabilities & ol\mbox{*} & We use COL\mbox{*}+NCOL\mbox{*} \\
    
    Net Operating Assets & noa\mbox{*} & We use OA\mbox{*}-OL\mbox{*} \\
    
    Long-Term NOA & lnoa\mbox{*} & \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/PPENT/}{PPENT} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/INTAN/}{INTAN} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/AO/}{AO} - \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/LO/}{LO} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/DP/}{DP} \\
    
    Liquid Current Assets & caliq\mbox{*} & We prefer to use CA\mbox{*} - \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/INVT/}{INVT}. If this is unavailable, we use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/CHE/}{CHE} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/RECT/}{RECT}  \\
    
    Property Plant and Equipment Less Inventories & ppeinv\mbox{*} & \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/PPEGT/}{PPEGT} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/INVT/}{INVT} \\
    
    Ortiz-Molina and Phillips Liquidity & aliq\mbox{*} & \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/CHE/}{CHE} + 0.75$\times$ COA\mbox{*} + 0.5(AT\mbox{*} - CA\mbox{*} - \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_balancesheetitems/INTAN/}{INTAN}). If INTAN is missing, we set it to zero \\

	\hline 
	\multicolumn{3}{|c|}{\textbf{Market Based}} \\
	\hline     

    Market Equity & me & We use the market equity for the stock we deem to the primary security of the firm. Importantly, we do not align the market value with the end of the fiscal period. Instead, we update the market value on a monthly basis and align it with the most recently available accounting characteristic \\
    
    Market Enterprise Value & mev\mbox{*} & We use ME\_COMPANY + NETDEBT\mbox{*} $\times$ FX\mbox{*} \\
    
    Market Assets & mat\mbox{*} & We use AT\mbox{*} $\times$ FX - BE\mbox{*} $\times$ FX + ME\_COMPANY \\

	\hline 
	\multicolumn{3}{|c|}{\textbf{Accruals}} \\
	\hline 
	
	Operating Accruals & oacc\mbox{*} & We prefer NI\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/OANCF/}{OANCF}. If that is unavailable, we use the yearly change in COWC\mbox{*}+the yearly change in NNCOA\mbox{*}\\
	
	Total Accruals & tacc\mbox{*} & We use OACC\mbox{*} + the yearly change in NFNA\mbox{*} \\
	
	Operating Cash Flow & ocf\mbox{*} & We prefer to use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/OANCF/}{OANCF}. If this is unavailable, we use NI\mbox{*}-OACC\mbox{*}. If this is unavailable, we use NI\mbox{*} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/DP/}{DP} - \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_global_daily_gfunda_dataitemsmz/WCAPT/}{WCAPT}. If WCAPT is missing, we use 0.\\
	
	Quarterly Operating Cash Flow & ocf\_qtr\mbox{*} & We use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/OANCF/}{OANCFQ}. If this is unavailable, then we use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/IB/}{IBQ} + \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/DP/}{DPQ} - \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_cashflowitems/WCAPCH/}{WCAPTQ}. If WCAPTQ is unavailable, we set it to \\
	
	Cash Based Operating Profitability & cop\mbox{*} & We prefer EBITDA\mbox{*}+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_incomestatementitems/XRD/}{XRD}-OACC\mbox{*}. If XRD is unavailable, we set it to zero \\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Other}} \\
	\hline 

    Employees in Thousands & emp & Compustat item \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_funda_miscellaneousitems/EMP/}{EMP} \\
\end{longtable}
}

{\scriptsize
\renewcommand{\arraystretch}{2}
\begin{longtable}{@{\extracolsep{\fill}}|p{6cm}|l|p{8cm}|@{}}
	\caption{Accounting Characteristics \label{accounting_char}}\\
	
	\hline
	Name & Abbreviation & Construction \\
	\hline
	\endfirsthead
	
	\hline
	Name & Abbreviation & Construction \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	\hline\hline
	\endlastfoot
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Accounting Based Size Measures}} \\
	\hline 	
	
	Assets & assets & $ AT\mbox{*}_t$\\
	
	Sales & sales & $SALE\mbox{*}_t$\\
	
	Book Equity & book\_equity & $BE\mbox{*}_t $\\
	
	Net Income & net\_income & $ NI\mbox{*}_t$\\
	
	Enterprise Value & enterprise\_value & $MEV\mbox{*}_t$ \\

	\hline 
	\multicolumn{3}{|c|}{\textbf{Growth - Percentage\footnote{This refers to all variables with a suffix of ``\_gr1" or ``\_gr3". The variables are percentage growth in the accounting variables before the suffix. The number in the suffix refers to either 1 or 3 year growth. For all variables, we only take the percentage growth if the denominator is above zero.}}} \\
	\hline 
	
	Asset Growth 1yr & at\_gr1 & $\frac{AT\mbox{*}_t}{AT\mbox{*}_{t-12}} - 1 $\\
	
	Sales Growth 1yr & sale\_gr1 & $\frac{SALE\mbox{*}_t}{SALE\mbox{*}_{t-12}} - 1 $\\
	
	Current Asset Growth 1yr & ca\_gr1 & $ \frac{CA\mbox{*}_t}{CA\mbox{*}_{t-12}} - 1 $\\
	
	Non-Current Asset Growth 1yr & nca\_gr1 & $ \frac{NCA\mbox{*}_t}{NCA\mbox{*}_{t-12}} - 1$\\
	
    Total Liabilities Growth 1yr & lt\_gr1 & $\frac{LT_t}{LT_{t-12}} - 1 $\\
	
	Current Liabilities Growth 1yr & cl\_gr1 & $\frac{CL\mbox{*}_t}{CL\mbox{*}_{t-12}} - 1 $ \\
	
	Non-Current Liabilities Growth 1yr & ncl\_gr1 & $\frac{NCL\mbox{*}_t}{NCL\mbox{*}_{t-12}} - 1 $\\
	
	Book Equity Growth 1yr & be\_gr1 & $\frac{BE\mbox{*}_t}{BE\mbox{*}_{t-12}} - 1 $ \\
	
	Preferred Stock Growth 1yr & pstk\_gr1 & $\frac{PSTK\mbox{*}_t}{PSTK\mbox{*}_{t-12}} - 1$\\
	
	Total Debt Growth 1yr & debt\_gr1 & $\frac{DEBT\mbox{*}_t}{DEBT\mbox{*}_{t-12}} - 1 $\\
	
	Cost of Goods Sold Growth 1yr & cogs\_gr1 & $\frac{COGS_t}{COGS_{t-12}} - 1 $\\
	
	Selling, General, and Administrative Expenses Growth 1yr & sga\_gr1 & $\frac{XSGA_t}{XSGA_{t-12}} - 1 $\\
	
	Operating Expenses Growth 1yr & opex\_gr1 & $ \frac{OPEX\mbox{*}_t}{OPEX\mbox{*}_{t-12}} - 1 $\\
	
	Asset Growth 3yr & at\_gr3 & $\frac{AT\mbox{*}_t}{AT\mbox{*}_{t-36}} - 1 $\\
	
	Sales Growth 3yr & sale\_gr3 & $\frac{SALE\mbox{*}_t}{SALE\mbox{*}_{t-36}} - 1 $\\
	
	Current Asset Growth 3yr & ca\_gr3 & $\frac{CA\mbox{*}_t}{CA\mbox{*}_{t-36}} - 1 $ \\
	
	Non-Current Asset Growth 3yr & nca\_gr3 & $\frac{NCA\mbox{*}_t}{NCA\mbox{*}_{t-36}} - 1$\\
	
	Total Liabilities Growth 3yr & lt\_gr3 & $\frac{LT_t}{LT_{t-36}} - 1 $\\
	
	Current Liabilities Growth 3yr & cl\_gr3 & $\frac{CL\mbox{*}_t}{CL\mbox{*}_{t-36}} - 1 $\\
	
	Non-Current Liabilities Growth 3yr & ncl\_gr3 & $\frac{NCL\mbox{*}_t}{NCL\mbox{*}_{t-36}} - 1 $\\
	
	Book Equity Growth 3yr & be\_gr3 & $ \frac{BE\mbox{*}_t}{BE\mbox{*}_{t-36}} - 1 $\\
	
	Preferred Stock Growth 3yr & pstk\_gr3 & $\frac{PSTK\mbox{*}_t}{PSTK\mbox{*}_{t-36}} - 1$\\
	
	Total Debt Growth 3yr & debt\_gr3 & $\frac{DEBT\mbox{*}_t}{DEBT\mbox{*}_{t-36}} - 1 $\\
	
	Cost of Goods Sold Growth 3yr & cogs\_gr3 & $\frac{COGS_t}{COGS_{t-36}} - 1 $\\
	
	Selling, General, and Administrative Expenses Growth 3yr & sga\_gr3 & $\frac{XSGA_t}{XSGA_{t-36}} - 1 $\\
	
	Operating Expenses Growth 3yr & opex\_gr3 & $\frac{OPEX\mbox{*}_t}{OPEX\mbox{*}_{t-36}} - 1 $\\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Growth - Changed Scaled by Total Assets}} \\
	\hline 	
	
	Gross Profit Change 1yr & gp\_gr1a & $\frac{GP\mbox{*}_t-GP\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
    
    Operating Cash Flow Change 1yr & ocf\_gr1a &$\frac{OCF\mbox{*}_t-OCF\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Cash and Short-Term Investments Change 1yr & cash\_gr1a &$\frac{CASH_t-CASH_{t-12}}{AT\mbox{*}_t}$ \\
	
	Inventory Change 1yr & inv\_gr1a &$ \frac{INV_t-INV_{t-12}}{AT\mbox{*}_t}$ \\
	
	Receivables Change 1yr & rec\_gr1a & $\frac{REC_t-REC_{t-12}}{AT\mbox{*}_t}$\\
	
	Property, Plans and Equiptment Gross Change 1yr & ppeg\_gr1a &$ \frac{PPEG_t-PPEG_{t-12}}{AT\mbox{*}_t}$\\
	
	Investment and Advances Change 1yr & lti\_gr1a &$\frac{LTI_t-LTI_{t-12}}{AT\mbox{*}_t}$\\
	
	Intangible Assets Change 1yr & intan\_gr1a &$ \frac{INTAN_t-INTAN_{t-12}}{AT\mbox{*}_t}$\\
	
	Short-Term Debt Change 1yr & debtst\_gr1a &$\frac{DEBTST_t-DEBTST_{t-12}}{AT\mbox{*}_t}$\\
	
	Accounts Payable Change 1yr & ap\_gr1a & $\frac{AP_t-AP_{t-12}}{AT\mbox{*}_t}$ \\
	
	Income Tax Payable Change 1yr & txp\_gr1a & $\frac{TXP_t-TXP_{t-12}}{AT\mbox{*}_t}$\\
	
	Long-Term Debt Change 1yr & debtlt\_gr1a &$\frac{DEBTLT_t-DEBTLT_{t-12}}{AT\mbox{*}_t}$\\
	
	Deferred Taxes and Investment Credit Change 1yr & txditc\_gr1a &$\frac{TXDITC\mbox{*}_t-TXDITC\mbox{*}_{t-12}}{AT\mbox{*}_t}$ \\
	
	Current Operating Assets Change 1yr & coa\_gr1a & $\frac{COA\mbox{*}_t-COA\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Current Operating Liabilities Change 1yr & col\_gr1a &$\frac{COL\mbox{*}_t-COL\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Current Operating Working Capital Change 1yr & cowc\_gr1a &$\frac{COWC\mbox{*}_t-COWC\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Non-Current Operating Assets Change 1yr & ncoa\_gr1a &$\frac{NCOA\mbox{*}_t-NCOA\mbox{*}_{t-12}}{AT\mbox{*}_t}$ \\
	
	Non-Current Operating Liabilities Change 1yr & ncol\_gr1a &$\frac{NCOL\mbox{*}_t-NCOL\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Net Non-Current Operating Assets Change 1yr & nncoa\_gr1a & $\frac{NNCOA\mbox{*}_t-NNCOA\mbox{*}_{t-12}}{AT\mbox{*}_t}$ \\
	
	Operating Assets Change 1yr & oa\_gr1a &$\frac{OA\mbox{*}_t-OA\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
    Operating Liabilities Change 1yr & ol\_gr1a &$ \frac{OL\mbox{*}_t-OL\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Net Operating Assets Change 1yr & noa\_gr1a &$ \frac{NOA\mbox{*}_t-NOA\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Financial Assets Change 1yr & fna\_gr1a &$\frac{FNA\mbox{*}_t-FNA\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Financial Liabilities Change 1yr & fnl\_gr1a &$\frac{FNL\mbox{*}_t-FNL\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Net Financial Assets Change 1yr & nfna\_gr1a &$\frac{NFNA\mbox{*}_t-NFNA\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
    Operating Profit before Depreciation Change 1yr & ebitda\_gr1a &$\frac{EBITDA\mbox{*}_t-EBITDA\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Operating Profit after Depreciation Change 1yr & ebit\_gr1a &$\frac{EBIT\mbox{*}_t-EBIT\mbox{*}_{t-12}}{AT\mbox{*}_t}$ \\
	
	Operating Earnings to Equity Change 1yr & ope\_gr1a &$\frac{OPE\mbox{*}_t-OPE\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Net Income Change 1yr & ni\_gr1a &$\frac{NI\mbox{*}_t-NI\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Depreciation and Amortization Change 1yr & dp\_gr1a &$\frac{DP_t-DP_{t-12}}{AT\mbox{*}_t}$\\
	
	Free Cash Flow Change 1yr & fcf\_gr1a &$\frac{FCF\mbox{*}_t-FCF\mbox{*}_{t-12}}{AT\mbox{*}_t}$ \\
	
	Net Working Capital Change 1yr & nwc\_gr1a &$\frac{NWC\mbox{*}_t-NWC\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Net Income Including Extraordinary Items Change 1yr & nix\_gr1a & $\frac{NIX\mbox{*}_t - NIX\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Equity Net Issuance Change 1yr & eqnetis\_gr1a & $\frac{EQNETIS\mbox{*}_t - EQNETIS\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Net Long-Term Debt Issuance Change 1yr & dltnetis\_gr1a & $\frac{DLTNETIS\mbox{*}_t - DLTNETIS\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Net Short-Term Debt Issuance Change 1yr & dstnetis\_gr1a & $\frac{DSTNETIS\mbox{*}_t - DSTNETIS\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
    Net Debt Issuance Change 1yr & dbnetis\_gr1a &$\frac{DBNETIS\mbox{*}_t - DBNETIS\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\

    Net Issuance Change 1yr & netis\_gr1a & $\frac{NETIS\mbox{*}_t - NETIS\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
    Financial Cash Flow Change 1yr & fincf\_gr1a &$\frac{FINCF\mbox{*}_t - FINCF\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\	
	
    Equity Net Payout Change 1yr & eqnpo\_gr1a & $\frac{EQNPO\mbox{*}_t - EQNPO\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
    Effective Tax Rate Change 1yr & tax\_gr1a & $\frac{TAX_t - TAX_{t-12}}{AT\mbox{*}_t}$\\
	
	Dividend Payout Ratio Change 1yr & div\_gr1a &$\frac{DIV\mbox{*}_t - DIV\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Equity Buyback Change 1yr & eqbb\_gr1a & $\frac{EQBB\mbox{*}_t - EQBB\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Equity Issuance Change 1yr & eqis\_gr1a & $\frac{EQIS\mbox{*}_t - EQIS\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
	Net Equity Payout Change 1yr & eqpo\_gr1a & $\frac{EQPO\mbox{*}_t - EQPO\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
	
    Capital Expenditures Change 1yr & capx\_gr1a &$\frac{CAPX_t - CAPX_{t-12}}{AT\mbox{*}_t}$\\
	
	Gross Profit Change 3yr & gp\_gr3a &$\frac{GP\mbox{*}_t-GP\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Operating Cash Flow Change 3yr & ocf\_gr3a &$\frac{OCF\mbox{*}_t-OCF\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Cash and Short-Term Investments Change 3yr & cash\_gr3a &$\frac{CASH_t-CASH_{t-36}}{AT\mbox{*}_t}$\\
	
	Inventory Change 3yr & inv\_gr3a & $ \frac{INV_t-INV_{t-36}}{AT\mbox{*}_t}$\\
	
	Receivables Change 3yr & rec\_gr3a &$\frac{REC_t-REC_{t-36}}{AT\mbox{*}_t}$\\
	
	Property, Plans and Equipment Gross Change 3yr & ppeg\_gr3a &$\frac{PPEG_t-PPEG_{t-36}}{AT\mbox{*}_t}$\\
	
	Investment and Advances Change 3yr & lti\_gr3a &$ \frac{LTI_t-LTI_{t-36}}{AT\mbox{*}_t}$\\
	
	Intangible Assets Change 3yr & intan\_gr3a &$\frac{INTAN_t-INTAN_{t-36}}{AT\mbox{*}_t}$\\
	
	Short-Term Debt Change 3yr & debst\_gr3a &$\frac{DEBTST_t-DEBTST_{t-36}}{AT\mbox{*}_t}$\\
	
	Accounts Payable Change 3yr & ap\_gr3a & $\frac{AP_t-AP_{t-36}}{AT\mbox{*}_t}$\\
	
	Income Tax Payable Change 3yr & txp\_gr3a &$\frac{TXP_t-TXP_{t-36}}{AT\mbox{*}_t}$\\
	
	Long-Term Debt Change 3yr & debtlt\_gr3a &$ \frac{DEBTLT_t-DEBTLT_{t-36}}{AT\mbox{*}_t}$ \\
	
	Deferred Taxes and Investment Credit Change 3yr & txditc\_gr3a &$\frac{TXDITC\mbox{*}_t-TXDITC\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Current Operating Assets Change 3yr & coa\_gr3a &$ \frac{COA\mbox{*}_t-COA\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Current Operating Liabilities Change 3yr & col\_gr3a &$ \frac{COL\mbox{*}_t-COL\mbox{*}_{t-36}}{AT\mbox{*}_t}$ \\
	
	Current Operating Working Capital Change 3yr & cowc\_gr3a &$\frac{COWC\mbox{*}_t-COWC\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Non-Current Operating Assets Change 3yr & ncoa\_gr3a &$\frac{NCOA\mbox{*}_t-NCOA\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Net Non-Current Operating Assets Change 3yr & nncoa\_gr3a &$\frac{NNCOA\mbox{*}_t-NNCOA\mbox{*}_{t-36}}{AT\mbox{*}_t}$ \\
	
	Operating Assets Change 3yr & oa\_gr3a &$\frac{OA\mbox{*}_t-OA\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Operating Liabilities Change 3yr & ol\_gr3a &$ \frac{OL\mbox{*}_t-OL\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Net Operating Assets Change 3yr & noa\_gr3a &$\frac{NOA\mbox{*}_t-NOA\mbox{*}_{t-36}}{AT\mbox{*}_t}$ \\
	
	Financial Assets Change 3yr & fna\_gr3a &$\frac{FNA\mbox{*}_t-FNA\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Financial Liabilities Change 3yr & fnl\_gr3a &$\frac{FNL\mbox{*}_t-FNL\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Net Financial Assets Change 3yr & nfna\_gr3a &$ \frac{NFNA\mbox{*}_t-NFNA\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Operating Profit before Depreciation Change 3yr & ebitda\_gr3a &$\frac{EBITDA\mbox{*}_t-EBITDA\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Operating Profit after Depreciation Change 3yr & ebit\_gr3a &$\frac{EBIT\mbox{*}_t-EBIT\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Operating Earnings to Equity Change 3yr & ope\_gr3a & $\frac{OPE\mbox{*}_t-OPE\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Net Income Change 3yr & ni\_gr3a &$ \frac{NI\mbox{*}_t-NI\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Depreciation and Amortization Change 3yr & dp\_gr3a &$\frac{DP_t-DP_{t-36}}{AT\mbox{*}_t}$\\
	
	Free Cash Flow Change 3yr & fcf\_gr3a &$\frac{FCF\mbox{*}_t-FCF\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Net Working Capital Change 3yr & nwc\_gr3a &$\frac{NWC\mbox{*}_t-NWC\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Inventory Change 1yr & inv\_gr3a &$\frac{INV_t-INV_{t-36}}{AT\mbox{*}_t}$\\
	
	Non-Current Operating Liabilities Change 3yr & ncol\_gr3a &$\frac{NCOL\mbox{*}_t-NCOL\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\	
	
	Net Income Including Extraordinary Items Change 3yr & nix\_gr3a &$\frac{NIX\mbox{*}_t-NIX\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
    Equity Net Issuance Change 3yr & eqnetis\_gr3a &$ \frac{EQNETIS\mbox{*}_t-EQNETIS\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Net Long-Term Debt Issuance Change 3yr & dltnetis\_gr3a &$\frac{DLTNETIS\mbox{*}_t-DLTNETIS\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Net Short-Term Debt Issuance Change 3yr & dstnetis\_gr3a &$\frac{DSTNETIS\mbox{*}_t-DSTNETIS\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Net Debt Issuance Change 3yr & dbnetis\_gr3a &$\frac{DBNETIS\mbox{*}_t-DBNETIS\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Net Issuance Change 3yr & netis\_gr3a &$\frac{NETIS\mbox{*}_t-NETIS\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Financial Cash Flow Change 3yr & fincf\_gr3a &$\frac{FINCF\mbox{*}_t-FINCF\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
	Net Working Capital Change 3yr & nwc\_gr3a &$\frac{NWC\mbox{*}_t-NWC\mbox{*}_{t-36}}{AT\mbox{*}_t}$\\
	
    Equity Net Payout Change 3yr & eqnpo\_gr3a & $ \frac{EQNPO\mbox{*}_t - EQNPO\mbox{*}_{t-36}}{AT\_t}$\\
	
    Effective Tax Rate Change 3yr & tax\_gr3a & $\frac{TAX_t - TAX_{t-36}}{AT\_t}$\\	
	
    Dividend Payout Ratio Change 3yr & div\_gr3a & $\frac{DIV\mbox{*}_t - DIV\mbox{*}_{t-36}}{AT\_t}$\\	
	
    Equity Buyback Change 3yr & eqbb\_gr3a & $\frac{EQBB\mbox{*}_t - EQBB\mbox{*}_{t-36}}{AT\_t}$\\	
	
    Equity Issuance Change 3yr & eqis\_gr3a & $\frac{EQIS\mbox{*}_t - EQIS\mbox{*}_{t-36}}{AT\_t}$\\

    Net Equity Payout Change 3yr & eqpo\_gr3a & $\frac{EQPO\mbox{*}_t - EQPO\mbox{*}_{t-36}}{AT\_t}$\\
	
    Capital Expenditures Change 3yr & capx\_gr3a & $\frac{CAPX_t - CAPX_{t-36}}{AT\_t}$\\	
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Investment}} \\
	\hline 	
	
	Capital Expenditures scaled by Assets & capx\_at &$\frac{CAPX_t}{AT\mbox{*}_t}$\\

    R\&D scaled by Assets & rd\_at &$\frac{XRD_t}{AT\mbox{*}_t}$\\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Non-Recurring Items}} \\
	\hline 	
	
	Special Items scaled by Assets & spi\_at &$\frac{SPI_t}{AT\mbox{*}_t}$ \\
	
	Extraordinary Items and Discontinued Operations scaled by Assets & xido\_at &$\frac{XIDO\mbox{*}_t}{AT\mbox{*}_t}$\\
	
	Non-Recurring Items scaled by Assets & nri\_at &$\frac{SPI_t+XIDO\mbox{*}_t}{AT\mbox{*}_t}$\\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Profit Margins}} \\
	\hline 
	
	Gross Profit Margin & gp\_sale &$\frac{GP\mbox{*}_t}{SALE\mbox{*}_t}$ \\ 
    
    Operating Profit Margin before Depreciation & ebitda\_sale &$\frac{EBITDA\mbox{*}_t}{SALE\mbox{*}_t}$\\
	
	Operating Profit Margin after Depreciation & ebit\_sale &$\frac{EBIT\mbox{*}_t}{SALE\mbox{*}_t}$\\
    
    Pretax Profit Margin & pi\_sale &$\frac{PI\mbox{*}_t}{SALE\mbox{*}_t}$\\
    
    Net Profit Margin before XI & ni\_sale &$\frac{NI\mbox{*}_t}{SALE\mbox{*}_t}$\\
    
    Net Profit Margin & nix\_sale &$\frac{NIX\mbox{*}_t}{SALE\mbox{*}_t}$\\
    
    Free Cash Flow Margin & fcf\_sale &$\frac{FCF\mbox{*}_t}{SALE\mbox{*}_t}$ \\

    Operating Cash Flow Margin & ocf\_sale &$\frac{OCF\mbox{*}_t}{SALE\mbox{*}_t}$\\

	\hline 
	\multicolumn{3}{|c|}{\textbf{Return on Assets}} \\
	\hline 
	
	Gross Profit scaled by Assets & gp\_at &$\frac{GP\mbox{*}_t}{AT\mbox{*}_t}$\\
	
	Operating Profit before Depreciation scaled by Assets & ebitda\_at &$\frac{EBITDA\mbox{*}_t}{AT\mbox{*}_t}$\\
	
	Operating Profit after Depreciation scaled by Assets & ebit\_at &$\frac{EBIT\mbox{*}_t}{AT\mbox{*}_t}$\\
	
	Firm Income scaled by Assets & fi\_at &$\frac{FI\mbox{*}_t}{AT\mbox{*}_t}$\\
	
	Cash Based Operating Profitability scaled by Assets & cop\_at &$\frac{COP\mbox{*}_t}{AT\mbox{*}_t}$ \\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Return on Book Equity}} \\
	\hline 	
	
	Operating Profit to Equity scaled by BE & ope\_be &$\frac{OPE\mbox{*}_t}{BE\mbox{*}_t}$\\
	
	Net Income scaled by BE & ni\_be &$\frac{NI\mbox{*}_t}{BE\mbox{*}_t}$\\
	
	Net Income Including Extraordinary Items scaled by BE & nix\_be &$\frac{NIX\mbox{*}_t}{BE\mbox{*}_t}$\\
	
	Operating Cash Flow scaled by BE & ocf\_be &$\frac{OCF\mbox{*}_t}{BE\mbox{*}_t}$\\
	
	Free Cash Flow scaled by BE & fcf\_be &$\frac{FCF\mbox{*}_t}{BE\mbox{*}_t}$\\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Return on Invested Capital}} \\
	\hline 	
	
	Gross Profit scaled by BEV & gp\_bev & $\frac{GP\mbox{*}_t}{BEV\mbox{*}_t}$ \\
	
	Operating Profit before Depreciation scaled by BEV & ebitda\_bev & $\frac{EBITDA\mbox{*}_t}{BEV\mbox{*}_t}$\\
    
    Operating Profit after Depreciation scaled by BEV & ebit\_bev &$ \frac{EBIT\mbox{*}_t}{BEV\mbox{*}_t}$ \\
    
    Firm Income scaled by BEV & fi\_bev &$\frac{FI\mbox{*}_t}{BEV\mbox{*}_t}$\\
    
	Cash Based Operating Profitability scaled by BEV & cop\_bev &$ \frac{COP\mbox{*}_t}{BEV\mbox{*}_t}$ \\
	
    \hline 
	\multicolumn{3}{|c|}{\textbf{Return on Physical Capital}} \\
	\hline 		
	
	Gross Profit scaled by PPEN & gp\_ppen &$\frac{GP\mbox{*}_t}{PPEN_t}$\\
    
	Operating Profit before Depreciation scaled by PPEN & ebitda\_ppen &$\frac{EBITDA\mbox{*}_t}{PPEN_t}$\\

	Free Cash Flow scaled by PPEN & fcf\_ppen &$ \frac{FCF\mbox{*}_t}{PPEN_t}$ \\
    
    \hline 
	\multicolumn{3}{|c|}{\textbf{Issuance}} \\
	\hline 
	
	Financial Cash Flow scaled by Assets & fincf\_at &$\frac{FINCF\mbox{*}_t}{AT\mbox{*}_t}$\\	
	
	Net Issuance scaled by Assets & netis\_at &$ \frac{NETIS\mbox{*}_t}{AT\mbox{*}_t}$\\
    
	Equity Net Issuance scaled by Assets & eqnetis\_at &$\frac{EQNETIS\mbox{*}_t}{AT\mbox{*}_t}$\\	
    
	Equity Issuance scaled by Assets & eqis\_at &$\frac{EQIS\mbox{*}_t}{AT\mbox{*}_t}$\\	
    
	Net Debt Issuance scaled by Assets & dbnetis\_at &$\frac{DBNETIS\mbox{*}_t}{AT\mbox{*}_t}$\\	
    
	Net Long-Term Debt Issuance scaled by Assets & dltnetis\_at &$\frac{DLTNETIS\mbox{*}_t}{AT\mbox{*}_t}$\\	
    
	Net Short-Term Debt Issuance scaled by Assets & dstnetis\_at &$ \frac{DSTNETIS\mbox{*}_t}{AT\mbox{*}_t}$ \\	
    
    \hline 
	\multicolumn{3}{|c|}{\textbf{Equity Payout}} \\
	\hline 
	
	Equity Net Payout scaled by Assets & eqnpo\_at &$\frac{EQNPO\mbox{*}_t}{AT\mbox{*}_t}$\\	
    
	Net Equity Payout scaled by Assets & eqbb\_at &$\frac{EQBB\mbox{*}_t}{AT\mbox{*}_t}$\\	
    
	Total Dividends scaled by Assets & div\_at &$\frac{DIV\mbox{*}_t}{AT\mbox{*}_t}$\\	    

    \hline 
	\multicolumn{3}{|c|}{\textbf{Accruals}} \\
	\hline 	
	
	Operating Accruals & oaccruals\_at &$\frac{OACC\mbox{*}_t}{AT\mbox{*}_t}$\\	
    
	Percent Operating Accruals & oaccruals\_ni &$\frac{OACC\mbox{*}_t}{|NIX\mbox{*}_t|}$\\
    
	Total Accruals & taccruals\_at &$ \frac{TACC\mbox{*}_t}{AT\mbox{*}_t}$ \\	
    
	Percent Total Accruals & taccruals\_ni &$\frac{TACC\mbox{*}_t}{|NIX\mbox{*}_t|}$\\	
    
	Net Operating Asset to Total Assets & noa\_at &$\frac{NOA\mbox{*}_t}{AT\mbox{*}_t}$ \\	
		
    \hline 
	\multicolumn{3}{|c|}{\textbf{Capitalization/Leverage Ratios}} \\
	\hline 	
	
	Common Equity scaled by BEV & be\_bev &$ \frac{BE\mbox{*}_t}{BEV\mbox{*}_t}$\\
    
    Total Debt scaled by BEV & debt\_bev &$\frac{DEBT\mbox{*}_t}{BEV\mbox{*}_t}$\\
    
    Cash and Short-Term Investments scaled by BEV & cash\_bev & $\frac{CASH_t}{BEV\mbox{*}_t}$\\
    
    Preferred Stock scaled by BEV & pstk\_bev &$\frac{PSTK\mbox{*}_t}{BEV\mbox{*}_t}$ \\
	
	Long-Term Debt scaled by BEV & debtlt\_bev &$\frac{DEBTLT_t}{BEV\mbox{*}_t}$ \\
	
	Short-Term Debt scaled by BEV & debtst\_bev &$\frac{DEBTST_t}{BEV\mbox{*}_t}$\\
    
    Total Debt scaled by MEV & debt\_mev &$\frac{DEBT\mbox{*}_t}{MEV\mbox{*}_t}$ \\
    
    Preferred Stock scaled by MEV & pstk\_mev &$\frac{PSTK\mbox{*}_t}{MEV\mbox{*}_t}$ \\
    
    Long-Term Debt scaled by MEV & debtlt\_mev &$ \frac{DEBTLT_t}{MEV\mbox{*}_t}$\\
    
    Short-Term Debt scaled by MEV & debtst\_mev &$\frac{DEBTST_t}{MEV\mbox{*}_t}$ \\
    
    \hline 
	\multicolumn{3}{|c|}{\textbf{Financial Soundness Ratios}} \\
	\hline 	
	
	Interest scaled by Total Debt & int\_debt & $\frac{INT_t}{DEBT\mbox{*}_t}$\\
    
    Interest scaled by Long-Term Debt & int\_debtlt &$\frac{INT_t}{DEBTLT_t}$ \\
    
    Operating Profit before Depreciation scaled by Total Debt & ebitda\_debt &$\frac{EBITDA\mbox{*}_t}{DEBT\mbox{*}_t}$ \\

    Profit before D\&A scaled by Current Liabilities & profit\_cl &$\frac{EBITDA\mbox{*}_t}{CL\mbox{*}_t}$ \\
    
    Operating Cash Flow scaled by Current Liabilities & ocf\_cl &$\frac{OCF\mbox{*}_t}{CL\mbox{*}_t}$ \\
    
    Operating Cash Flow scaled by Total Debt & ocf\_debt &$\frac{OCF\mbox{*}_t}{DEBT\mbox{*}_t}$ \\
	
	Cash Balance scaled by Total Liabilities & cash\_lt &$\frac{CASH_t}{LT_t}$ \\
    
    Inventory scaled by Current Assets & inv\_act &$ \frac{INV_t}{ACT_t}$\\
    
    Receivables scaled by Current Assets & rec\_act &$\frac{REC_t}{ACT_t}$ \\
    
    Short-Term Debt scaled by Total Debt & debtst\_debt &$\frac{DEBTST_t}{DEBT\mbox{*}_t}$\\
    
    Current Liabilities scaled by Total Liabilities & cl\_lt &$\frac{CL\mbox{*}_t}{LT_t}$ \\
    
    Long-Term Debt scaled by Total Debt & debtlt\_debt &$\frac{DEBTLT_t}{DEBT\mbox{*}_t}$ \\
	
	Operating Leverage & opex\_at &$\frac{OPEX\mbox{*}_t}{AT\mbox{*}_t}$ \\
    
    Free Cash Flow scaled by Operating Cash Flow & fcf\_ocf &$ \frac{FCF\mbox{*}_t}{OCF\mbox{*}_t}$ \\
  
     Total Liabilities scaled by Total Tangible Assets & lt\_ppen &$\frac{LT_t}{PPEN_t}$\\  
    
     Long-Term Debt to Book Equity & debtlt\_be &$\frac{DEBTLT_t}{BE\mbox{*}_t}$ \\
    
     Working Capital scaled by Assets & nwc\_at &$\frac{NWC\mbox{*}_t}{AT\mbox{*}_t}$\\
  
    \hline 
	\multicolumn{3}{|c|}{\textbf{Solvency Ratios}} \\
	\hline 	
	
	Debt-to-Assets & debt\_at &$\frac{DEBT\mbox{*}_t}{AT\mbox{*}_t}$ \\
    
    Debt to Shareholders' Equity Ratio & debt\_be &$\frac{DEBT\mbox{*}_t}{BE\mbox{*}_t}$ \\
    
    Interest Coverage Ratio & ebit\_int &$\frac{EBIT\mbox{*}_t}{INT_t}$\\

    \hline 
	\multicolumn{3}{|c|}{\textbf{Liquidity Ratios}} \\
	\hline
	
	Days Inventory Outstanding & inv\_days &$ \frac{\frac{INV_t+INV_{t -12}}{2}}{COGS_t}\times365$\\
    
    Days Sales Outstanding & rec\_days &$\frac{\frac{REC_t+REC_{t -12}}{2}}{SALE\mbox{*}_t}\times365$\\
    
    Days Accounts Payable Outstanding & ap\_days &$\frac{\frac{AP_t+AP_{t -12}}{2}}{COGS_t}\times365$\\
    
    Cash Conversion Cycle & cash\_conversion &$ INV\_DAYS_t+REC\_DAYS_t-AP\_DAYS_t$ \\
    
    Cash Ratio & cash\_cl &$\frac{CASH_t}{CL\mbox{*}_t}$ \\
    
    Quick Ratio & caliq\_cl &$ \frac{CALIQ\mbox{*}_t}{CL\mbox{*}_t}$\\
    
    Current Ratio & ca\_cl &$\frac{CA\mbox{*}_t}{CL\mbox{*}_t}$ \\
    
    \hline 
	\multicolumn{3}{|c|}{\textbf{Activity/Efficiency Ratios}} \\
	\hline 
	
	Inventory Turnover & inv\_turnover &$\frac{COGS_t}{(INV_t+INV_{t -12})/2}$ \\
    
    Asset Turnover & at\_turnover &$\frac{SALE\mbox{*}_t}{(AT\mbox{*}_t+AT\mbox{*}_{t -12})/2}$\\
	
	Receivables Turnover & rec\_turnover & $\frac{SALE\mbox{*}_t}{(REC_t+REC_{t -12})/2}$ \\

    Account Payables Turnover & ap\_turnover &$\frac{COGS_t+INV_t-INV_{t-12}}{(AP_t+AP_{t -12})/2}$\\

    \hline 
	\multicolumn{3}{|c|}{\textbf{Miscellaneous}} \\
	\hline     
	
	Advertising scaled by Sales & adv\_sale &$\frac{XAD_t}{SALE\mbox{*}_t}$ \\
	
	Labor Expense scaled by Sales & staff\_sale &$\frac{XLR_t}{SALE\mbox{*}_t}$ \\
	
	Sales scaled by BEV & sale\_bev &$\frac{SALE\mbox{*}_t}{BEV\mbox{*}_t}$ \\
	
	R\&D scaled by Sales & rd\_sale &$\frac{XRD_t}{SALE\mbox{*}_t}$\\
	
	Sales scaled by Total Stockholders' Equity & sale\_be &$\frac{SALE\mbox{*}_t}{BE\mbox{*}_t}$ \\
	
	Dividend Payout Ratio & div\_ni &$\frac{DVC_t}{NI\mbox{*}_t}$ \\
	
	Sales scaled by Working Capital & sale\_nwc &$\frac{SALE\mbox{*}_t}{NWC\mbox{*}_t}$\\
	
	Effective Tax Rate & tax\_pi &$ \frac{TAX_t}{PI\mbox{*}_t}$ \\
	
    \hline 
	\multicolumn{3}{|c|}{\textbf{Balance Sheet Fundamental to Market Equity}} \\
	\hline   	
	
	Book Equity scaled by Market Equity & be\_me &$\frac{BE\mbox{*}_t}{ME_t}$\\
	
	Total Assets scaled by Market Equity & at\_me &$ \frac{AT\mbox{*}_t}{ME_t}$\\
	
	Cash and Short-Term Investments scaled by Market Equity & cash\_me &$\frac{CASH_t}{ME_t}$\\
	
    \hline 
	\multicolumn{3}{|c|}{\textbf{Income Fundamentals to Market Equity}} \\
	\hline  	
    
    Gross Profit scaled by ME & gp\_me &$\frac{GP\mbox{*}_t}{ME_t}$ \\
	
	Operating Profit before Depreciation scaled by ME & ebitda\_me &$\frac{EBITDA\mbox{*}_t}{ME_t}$\\
	
	Operating Profit after Depreciation scaled by ME & ebit\_me &$\frac{EBIT\mbox{*}_t}{ME_t}$\\
	
	Operating Earnings to Equity scaled by ME & ope\_me &$\frac{OPE\mbox{*}_t}{ME_t}$\\
	
	Net Income scaled by ME & ni\_me &$\frac{NI\mbox{*}_t}{ME_t}$ \\
	
	Sales scaled by ME & sale\_me &$\frac{SALE\mbox{*}_t}{ME_t}$\\
	
	Operating Cash Flow scaled by ME & ocf\_me &$\frac{OCF\mbox{*}_t}{ME_t}$\\
	
	Free Cash Flow scaled by ME & fcf\_me &$\frac{FCF\mbox{*}_t}{ME_t}$ \\
	
	Net Income Including Extraordinary Items scaled by ME & nix\_me &$\frac{NIX\mbox{*}_t}{ME_t}$\\
	
	Cash Based Operating Profitability scaled by ME & cop\_me &$\frac{COP\mbox{*}_t}{ME_t}$\\
	
	R\&D scaled by ME & rd\_me &$ \frac{XRD_t}{ME_t}$\\
	
    \hline 
	\multicolumn{3}{|c|}{\textbf{Balance Sheet Fundamentals to Market Enterprise Value}} \\
	\hline 	
	
	Book Equity scaled by MEV & be\_mev &$\frac{BE\mbox{*}_t}{MEV\mbox{*}_t}$ \\

    Total Assets scaled by MEV & at\_mev &$\frac{AT\mbox{*}_t}{MEV\mbox{*}_t}$ \\
	
    Cash and Short-Term Investments scaled by MEV & cash\_mev &$\frac{CASH_t}{MEV\mbox{*}_t}$ \\
	
    Book Enterprise Value scaled by MEV & bev\_mev &$\frac{BEV\mbox{*}_t}{MEV\mbox{*}_t}$ \\
	
    Property, Plans and Equipment Net scaled by MEV & ppen\_mev &$\frac{PPEN_t}{MEV\mbox{*}_t}$ \\
	
    \hline 
	\multicolumn{3}{|c|}{\textbf{Equity Payout/Issuance to Market Equity}} \\
	\hline 	

    Total Dividends scaled by ME & div\_me &$\frac{DIV\mbox{*}_t}{ME_t}$ \\
	
    Equity Buyback scaled by ME & eqbb\_me &$\frac{EQBB\mbox{*}_t}{ME_t}$ \\
	
    Equity Issuance scaled by ME & eqis\_me &$\frac{EQIS\mbox{*}_t}{ME_t}$ \\
	
    Net Equity Payout scaled by ME & eqpo\_me &$\frac{EQPO\mbox{*}_t}{ME_t}$\\
	
   Equity Net Payout scaled by ME & eqnpo\_me &$\frac{EQNPO\mbox{*}_t}{ME_t}$\\
	
    Equity Net Issuance scaled by ME & eqnetis\_me &$\frac{EQNETIS\mbox{*}_t}{ME_t}$ \\

    \hline 
	\multicolumn{3}{|c|}{\textbf{Debt Issuance to Market Enterprise Value}} \\
	\hline 
	
    Net Long-Term Debt Issuance scaled by MEV & dltnetis\_mev &$\frac{DLTNETIS\mbox{*}_t}{MEV\mbox{*}_t}$\\	
	
    Net Short-Term Debt Issuance scaled by MEV & dstnetis\_mev &$\frac{DSTNETIS\mbox{*}_t}{MEV\mbox{*}_t}$ \\
	
    Net Debt Issuance scaled by MEV & dbnetis\_mev &$\frac{DBNETIS\mbox{*}_t}{MEV\mbox{*}_t}$\\
	
    \hline 
	\multicolumn{3}{|c|}{\textbf{Firm Payout/Issuance to Market Enterprise Value}} \\
	\hline 	
	
    Net Issuance scaled by MEV & netis\_mev &$\frac{NETIS\mbox{*}_t}{MEV\mbox{*}_t}$ \\
	
    \hline 
	\multicolumn{3}{|c|}{\textbf{Income Fundamentals to Market Enterprise Value}} \\
	\hline 		
	
	Gross Profit scaled by MEV & gp\_mev &$\frac{GP\mbox{*}_t}{MEV\mbox{*}_t}$ \\
	
	Operating Profit before Depreciation scaled by MEV & ebitda\_mev &$\frac{EBITDA\mbox{*}_t}{MEV\mbox{*}_t}$\\
	
	Operating Profit after Depreciation scaled by MEV & ebit\_mev &$\frac{EBIT\mbox{*}_t}{MEV\mbox{*}_t}$\\
	
	Sales scaled by MEV & sale\_mev &$\frac{SALE\mbox{*}_t}{MEV\mbox{*}_t}$\\
	
	Operating Cash Flow scaled by MEV & ocf\_mev & $\frac{OCF\mbox{*}_t}{MEV\mbox{*}_t}$ \\
    
    Free Cash Flow scaled by MEV & fcf\_mev &$\frac{FCF\mbox{*}_t}{MEV\mbox{*}_t}$\\
    
    Cash Based Operating Profitability scaled by MEV & cop\_mev &$\frac{COP\mbox{*}_t}{MEV\mbox{*}_t}$ \\
	
    Financial Cash Flow Change scaled by MEV & fincf\_mev &$\frac{FINCF\mbox{*}_t}{MEV\mbox{*}_t}$\\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{New Variables not in HXZ}} \\
	\hline 
	
	Net Income to Sales Quarterly Volatility & niq\_saleq\_std &$\sigma_{8Q}\left(\frac{NI\_QTR\mbox{*}_t}{SALE\_QTR\mbox{*}_t}\right)$\\
	
	Net Income scaled by Employees & ni\_emp & $\frac{NI\mbox{*}_t}{EMP_t}$\\
	
	Sales scaled by Employees & sale\_emp &$\frac{SALE\mbox{*}_t}{EMP_t}$ \\
	
	Net Income scaled by Assets & ni\_at &$\frac{NI\mbox{*}_t}{AT\mbox{*}_t}$ \\
    
    Operating Cash Flow scaled by Assets & ocf\_at &$\frac{OCF\mbox{*}_t}{AT\mbox{*}_t}$ \\
    
    Operating Cash Flow to Assets 1 yr Change  & ocf\_at\_chg1 &$OCF\_AT_t - OCF\_AT_{t-12}$ \\
    
    Quarterly ROE Volatility & roeq\_be\_std & $\sigma_{16Q}\left(\frac{NI\_QTR\mbox{*}_t}{BE\mbox{*}_t}\right)$ \\
    
    ROE Volatility & roe\_be\_std & $\sigma_{60M}\left(\frac{NI\mbox{*}_t}{BE\mbox{*}_t}\right)$ \\  
    
    Gross Product to Assets 5 yr Change & gpoa\_ch5 & $\frac{GP\mbox{*}_t}{AT\mbox{*}_t} - \frac{GP\mbox{*}_{t-60}}{AT\mbox{*}_{t-60}}$ \\
    
    ROE 5 yr Change & roe\_ch5 & $\frac{NI\mbox{*}_t}{BE\mbox{*}_t} - \frac{NI\mbox{*}_{t-60}}{BE\mbox{*}_{t-60}}$ \\
    
    ROA 5 yr Change & roa\_ch5 & $\frac{NI\mbox{*}_t}{AT\mbox{*}_t} - \frac{NI\mbox{*}_{t-60}}{AT\mbox{*}_{t-60}}$\\
    
    Operating Cash Flow to Assets 5 yr Change & cfoa\_ch5 & $\frac{OCF\mbox{*}_t}{AT\mbox{*}_t} - \frac{OCF\mbox{*}_{t-60}}{AT\mbox{*}_{t-60}}$\\
    
    Gross Product to Sales 5 yr Change & gmar\_ch5 & $\frac{GP\mbox{*}_t}{SALE\mbox{*}_t} - \frac{GP\mbox{*}_{t-60}}{SALE\mbox{*}_{t-60}}$\\
	
    \hline 
	\multicolumn{3}{|c|}{\textbf{New Variables from HXZ}} \\
	\hline 		
	
    Cash and Short Term Investments scaled by Assets & cash\_at &$\frac{CASH_t}{AT\mbox{*}_t}$ \\
	
	Number of Consecutive Earnings Increases & ni\_inc8q &
	Count number of earnings increases over past 8 quarters \\
	
	Change in Property, Plant and Equipment Less Inventories scaled by lagged Assets & ppeinv\_gr1a &$\frac{PPEINV\mbox{*}_t - PPEINV\mbox{*}_{t-12}}{AT\mbox{*}_{t-12}}$\\
	
	Change in Long-Term NOA scaled by average Assets & lnoa\_gr1a & $ \frac{LNOA\mbox{*}_t - LNOA\mbox{*}_{t-12}}{AT\mbox{*}_t - AT\mbox{*}_{t-12}}$\\
	
	CAPX 1 year growth & capx\_gr1 & $\frac{CAPX_t}{CAPX_{t-12}} - 1$\\
	
	CAPX 2 year growth & capx\_gr2 & $\frac{CAPX_t}{CAPX_{t-24}} - 1$\\
	
	CAPX 3 year growth & capx\_gr3 & $ \frac{CAPX_t}{CAPX_{t-36}} - 1$ \\
	
	Change in Short-Term Investments scaled by Assets & sti\_gr1a &$ \frac{IVST_t - IVST_{t-12}}{AT\mbox{*}_t} $\\
	
	Quarterly Income scaled by BE & niq\_be & $\frac{NI\_QTR\mbox{*}_t}{BE\mbox{*}_{t-3}}$\\
	
	Change in Quarterly Income scaled by BE & niq\_be\_chg1 &$ NIQ\_BE_t - NIQ\_BE_{t-12}$\\
	
	Quarterly Income scaled by AT & niq\_at & $\frac{NI\_QTR\mbox{*}_t}{AT\mbox{*}_{t-3}}$\\
	
	Change in Quarterly Income scaled by AT & niq\_at\_chg1 &$NIQ\_AT_t - NIQ\_AT_{t-12}$\\
	
	Quarterly Sales Growth & saleq\_gr1 & $\frac{SALE\_QTR\mbox{*}_t}{SALE\_QTR\mbox{*}_{t-12}} - 1$ \\
	
	R\&D Capital-to-Assets & rd5\_at & $\frac{\sum_{n = 0}^4 (1 - .2\times n)(XRD_{t-12*n})}{AT\mbox{*}_t}$ \\
	
	Age & age & Age of the firms in months \\
	
	Change Sales minus Change Inventory & dsale\_dinv & $ CHG\_TO\_EXP(SALE\mbox{*}_t) - CHG\_TO\_EXP(INV_t)$\\
	
	Change Sales minus Change Receivables & dsale\_drec & $CHG\_TO\_EXP(SALE\mbox{*}_t) - CHG\_TO\_EXP(REC_t)$\\	
	
	Change Gross Profit minus Change Sales & dgp\_dsale & $ CHG\_TO\_EXP(GP\mbox{*}_t) - CHG\_TO\_EXP(SALE\mbox{*}_t)$\\
	
	Change Sales minus Change SG\&A & dsale\_dsga & $ CHG\_TO\_EXP(SALE\mbox{*}_t) - CHG\_TO\_EXP(XSGA_t)$\\
	
	Earnings Surprise & saleq\_su & $ SUR(SALE\_QTR\mbox{*})$\\
    
    Revenue Surprrise & niq\_su &$ SUR(NI\_QTR\mbox{*})$\\
    
    Total Debt scaled by ME & debt\_me &$\frac{DEBT\mbox{*}_t}{ME_t}$\\
    
    Net Debt scaled by ME & netdebt\_me &$\frac{NETDEBT\mbox{*}_t}{ME_t}$\\
    
	Abnormal Corporate Investment & capex\_abn &
	$
	{\scriptscriptstyle \frac{CAPX\_SALE\mbox{*}_t}{(CAPX\_SALE\mbox{*}_{t-12} + CAPX\_SALE\mbox{*}_{t-24} + CAPX\_SALE\mbox{*}_{t-36})/3} - 1}
	$
	\\
    
    Inventory Change 1 yr & inv\_gr1 & $\frac{INV_t}{INV_{t-12}} - 1$ \\
    
    Book Equity Change 1 yr scaled by Assets & be\_gr1a &$\frac{BE\mbox{*}_t - BE\mbox{*}_{t-12}}{AT\mbox{*}_t}$\\
    
    Ball Operating Profit to Assets & op\_at &$ \frac{OP\mbox{*}_t}{AT\mbox{*}_t}$\\
    
    Earnings before Tax and Extraordinary Items to Net Income Including Extraordinary Items & pi\_nix &$\frac{PI\mbox{*}_t}{NIX\mbox{*}_t}$ \\
    
    Ball Operating Profit scaled by lagged Assets & op\_atl1 & $\frac{OP\mbox{*}_t}{AT\mbox{*}_{t-12}}$\\
    
    Operating Profit scaled by lagged Book Equity & ope\_bel1 &$\frac{OPE\mbox{*}_t}{BE\mbox{*}_{t-12}}$ \\
    
    Gross Profit scaled by lagged Assets & gp\_atl1 &$\frac{GP\mbox{*}_t}{AT\mbox{*}_{t-12}}$ \\
    
    Cash Based Operating Profitability scaled by lagged Assets & cop\_atl1 &$\frac{COP\mbox{*}_t}{AT\mbox{*}_{t-12}}$\\
    
    Book Leverage & at\_be & $\frac{AT\mbox{*}_t}{BE\mbox{*}_t}$\\
    
    Operating Cash Flow to Sales Quarterly Volatility & ocfq\_saleq\_std & $\sigma_{16Q}\left(\frac{OCF\_QTR\mbox{*}_t}{SALE\_QTR\mbox{*}_t})\right)$ \\
    
    Liquidity scaled by lagged Assets & aliq\_at &$\frac{ALIQ\mbox{*}_t}{AT\mbox{*}_{t-12}}$ \\
    
    Liquidity scaled by lagged Market Assets & aliq\_mat & $\frac{ALIQ\mbox{*}_t}{MAT\mbox{*}_{t-12}}$\\
    
    Tangibility & tangibility &$\frac{CASH_t + 0.715\times REC_t + 0.547\times INV_t + 0.535\times PPEG_t}{AT\mbox{*}_t}$\\
    
    \hypertarget{eq_dur2}{Equity Duration} & eq\_dur & Outlined in detail \hyperlink{eq_dur}{here} \\
    
    \hypertarget{pio2}{Piotroski F-Score} & f\_score & Outlined in detail \hyperlink{pio}{here} \\
    
    \hypertarget{ohl2}{Ohlson O-Score} & o\_score & Outlined in detail \hyperlink{ohl}{here} \\
    
    \hypertarget{alt2}{Altman Z-Score} & z\_score & Outlined in detail \hyperlink{alt}{here} \\
    
    \hypertarget{kap2}{Kaplan-Zingales Index} & kz\_index & Outlined in detail \hyperlink{kap}{here} \\
    
    \hypertarget{intval2}{Intrinsic Value} & intrinsic\_value & Outlined in detail \hyperlink{intval}{here} \\
    
    Intrinsic value-to-market & ival\_me &
    $\frac{INTRINSIC\_VALUE\mbox{*}_t}{ME_t}$ \\
    
    Sales scaled by Employees Growth 1 yr & sale\_emp\_gr1 & $\frac{SALE\_EMP_t}{SALE\_EMP_{t-12}} - 1$\\
    
    Employee Growth 1 yr & emp\_gr1 &$\frac{EMP_t - EMP_{t-12}}{0.5\times EMP_t + 0.5\times EMP_{t-12}}$\\
    
    Earnings Variability & earnings\_variability &$\frac{\sigma_{60M}\left(NI\mbox{*}_t/AT\mbox{*}_{t-12}\right)}{\sigma_{60M}\left(OCF\mbox{*}_t/AT\mbox{*}_{t-12}\right)}$\\
    
    1 yr lagged Net Income to Assets & ni\_ar1 &$
    {
         \frac{cov((NI\mbox{*}/AT\mbox{*})_t, (NI\mbox{*}/AT\mbox{*})_{t-12})}{var((NI\mbox{*}/AT\mbox{*})_{t-12})}
    }
$\\
    
    \hypertarget{ni_ivol2}{Net Income Idiosyncratic Volatility} & ni\_ivol & Outlined in detail \hyperlink{ni_ivol}{here}\\
\end{longtable}
}


\section{Market Based Characteristics}
\textbf{Datasets}
\begin{itemize}
	\item CRSP.MSF
	\item CRSP.DSF
	\item COMP.SECD
	\item COMP.G\_SECD
	\item COMP.SECM
	\item COMP.SECURITY
	\item COMP.G\_SECURITY
\end{itemize}

\noindent\textbf{Market Variables}

%The abbreviation is used to refer to the market variable. 
\noindent A suffix of '\mbox{*}' indicates that we have altered or renamed the original item. 

\setlength\LTcapwidth{\textwidth} % default: 4in (rather less than \textwidth...)      

\setlength\LTleft{0pt}            % default: \fill
\setlength\LTright{0pt}           % default: \fill    

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|m{5cm}|l|m{8cm}|@{}}
		\caption{Market Variables \label{market_var}}\\
	
	\hline
	Name & Abbreviation & Construction \\
	\hline
	\endfirsthead
	
	\hline
	Name & Abbreviation & Construction \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	\hline\hline
	\endlastfoot
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{CRSP Variables\footnote{lag is a lag function where lag(x) is the value of x from the previous time period}}} \\

	\hline 
	
    Share Adjustment Factor & adjfct\mbox{*} & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_distributioninformation/cfacshr/}{CFACSHR}\\
    
    Shares & shares\mbox{*} & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_shareinformation/shrout/}{SHROUT}/1000 so shares outstanding are in millions. \\
    
    Price & prc\mbox{*} & We use
    $|$\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_timeseriesinformation/prc/}{PRC}$|$\\
    
    Local Price & prc\_local\mbox{*} & We use PRC\mbox{*}\\
    
    Highest Daily Price & prc\_high & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_dsf_timeseriesinformation/askhi/}{ASKHI}. If PRC\mbox{*} or AKSHI are negative, then PRC\_HIGH is set to missing \\
    
    Lowest Daily Price & prc\_low & We use
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_dsf_timeseriesinformation/bidlo/}{BIDLO}. If PRC\mbox{*} or BIDLO are negative, then PRC\_LOW is set to missing \\
    
    % Adjusted Proce & prc\_adj\mbox{*} & We use PRC\mbox{*}$\times$ADJFCT\mbox{*} \\
    
    Market Equity & me\mbox{*} & We use PRC\mbox{*}$\times$SHARES\mbox{*} so market equity is quoted in million USD. \\
    
    Company Market Equity & me\_company\mbox{*} & We sum ME\mbox{*} grouped by 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_identifyinginformation/permco/}{PERMCO} and date\\
    
    Trading Volume & tvol\mbox{*} & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_timeseriesinformation/vol/}{VOL} \\
    
    Dollar Volume & dolvol\mbox{*} & We use 
    TVOL\mbox{*}$\times$PRC\mbox{*}\\
    
    Return & RET\mbox{*} & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_timeseriesinformation/ret/}{RET}. In case of delisting, we calculate as (1+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_timeseriesinformation/ret/}{RET})*(1+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/crsp_m_stock/dsedelist/dlret/}{DLRET})-1\\
    
    Local Return & ret\_local\mbox{*} & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_timeseriesinformation/ret/}{RET}. In case of delisting, we calculate as (1+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_timeseriesinformation/ret/}{RET})*(1+\href{https://wrds-www.wharton.upenn.edu/data-dictionary/crsp_m_stock/dsedelist/dlret/}{DLRET})-1\\
    
    Excess Return & ret\_exc\mbox{*} & We use RET\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/crsp_a_indexes/mcti/#row-t30ret}{T30RET}/21. If T30RET is unavailable, we use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/ff_all/factors_monthly/#row-rf}{RF}. If the return is a monthly return rather than a daily return, the T30RET is divided by 1 rather than 21. \\
    
    Excess Return t+1 & ret\_exc\_lead1m\mbox{*} &  Excess return (ret\_exc\mbox{*}) in month t+1 \\

    Time Since Most Recent Return & ret\_lag\_dif\mbox{*} & We automatically set this to 1 \\
    
    Cumulative Return & ri\mbox{*} & This is the cumulative return estimated from RET\mbox{*}\\
    
    Monthly Dividend & div\_tot\mbox{*} & We use\newline
    (\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_timeseriesinformation/ret/}{RET} -\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_timeseriesinformation/retx/}{RETX})$\times$lag(PRC\mbox{*})$\times$(\href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/crsp_a_stock_msf_distributioninformation/cfacshr/}{CFACSHR}/lag(CFACSHR))  \\
    
	\hline 
	\multicolumn{3}{|c|}{\textbf{Compustat Variables}} \\
 
	\hline
	
    Share Adjustment Factor & adjfct\mbox{*} & We use \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_secd_dataitems/AJEXDI/}{AJEXDI}\\
    
    Shares & shares\mbox{*} & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_secd_dataitems/CSHOC/}{CSHOC}/1000000\\
    
    Price & prc\mbox{*} & We use PRC\_LOCAL\mbox{*}$\times$FX \\
    
    Local Price & prc\_local\mbox{*} & We use PRCCD\\
    
    Market Equity & me\mbox{*} & We use PRC\mbox{*}$\times$SHARES\mbox{*} \\
    
    Company Market Equity & me\_company\mbox{*} & We use ME\mbox{*} \\
    
    Trading Volume & tvol\mbox{*} & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_secd_dataitems/CSHTRD/}{CSHTRD}\\
    
    Dollar Volume & dolvol\mbox{*} & We use 
    TVOL\mbox{*}$\times$PRC\mbox{*}\\
    
    Cumulative Return - Local & ri\_local\mbox{*} & We use
    PRC\_LOCAL\mbox{*}$\times$ \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_secd_dataitems/TRFD/}{TRFD}/AJEXDI \\
    
    Local Return & ret\_local\mbox{*} & We use RI\_LOCAL\mbox{*}/lag(RI\_LOCAL\mbox{*}) - 1. In case of delisting, we calculate as (RI\_LOCAL\mbox{*}/lag(RI\_LOCAL\mbox{*}) * (1+dlret\footnote{dlret is set to -0.3 when \href{https://wrds-www.wharton.upenn.edu/data-dictionary/comp_na_daily_all/security/dlrsni/}{dlsrni} is '02' or '03' and set to 0 otherwise}) - 1)\\
    
    Cumulative Return & ri\mbox{*} & RI\_LOCAL\mbox{*} $\times$ FX\mbox{*}\\
    
    Return & RET\mbox{*} & We use RI\mbox{*}/lag(RI\mbox{*}) - 1. In case of delisting, we calculate as (RI\mbox{*}/lag(RI\mbox{*}) * (1+dlret) -1)\\
    
    Excess Return & ret\_exc\mbox{*} & We use RET\mbox{*}-\href{https://wrds-www.wharton.upenn.edu/data-dictionary/crsp_a_indexes/mcti/#row-t30ret}{T30RET}/21. If T30RET is unavailable, we use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/ff_all/factors_monthly/#row-rf}{RF}. If the return is a monthly return rather than a daily return, the T30RET is divided by 1 rather than 21. \\
    
    Excess Return t+1 & ret\_exc\_lead1m\mbox{*} &  Excess return (ret\_exc\mbox{*}) in month t+1 \\
    
    Time Since Most Recent Return  & ret\_lag\_dif\mbox{*} & We estimate the number of days since the previous return. If the returns are monthly rather than daily, then the time is in months\\
 
    
    Monthly Dividend & div\_tot\mbox{*} & We use DIV $\times$ FX\mbox{*}. If DIV is missing, we set it to zero\\
    
    Cash Dividend & div\_cash\mbox{*} & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_secd_dataitems/DIVD/}{DIVD} $\times$ FX\mbox{*}. If DIVD is unavailable, we set it to zero \\
    
    Special Cash Dividend & div\_spc\mbox{*} & We use 
    \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_secd_dataitems/DIVSP/}{DIVSP} $\times$ FX\mbox{*}. If DIVSP is unavailable, we set it to zero \\
    
    Bid-Ask Average Dummy & bidask\mbox{*} & When \href{https://wrds-www.wharton.upenn.edu/data-dictionary/form_metadata/comp_na_daily_all_secd_dataitems/PRCSTD/}{PRCSTD} = 4 then 1, otherwise 0 \\
    
	\hline 
	\multicolumn{3}{|c|}{\textbf{Asset Pricing Factors}} \\
	\hline 
	
	Excess Market Return & mktrf\mbox{*} & Country specific market return \\
		
	High Minus Low & hml\mbox{*} & Country specific factor following Fama and French (1993) and using breakpoints from non-micro cap stocks within the country \\
		
	Small Minus Big ala Fama-French & smb\_ff\mbox{*} & Average of small portfolios minus average of large portfolios from  hml\mbox{*} \\
		
	Return on Equity & roe\mbox{*} & Country specific factor following Hou, Xue and Zhang (2015) and using breakpoints from non-micro cap stocks within the country. We use double sorts on return on equity and size rather than triple sorts with investment, due to the limited number of stocks in some international markets. \\
		
	Investment & inv\mbox{*} & Country specific factor following Hou, Xue and Zhang (2015) and using breakpoints from non-micro cap stocks within the country. We use double sorts on investment and size rather than triple sorts with return on equity, due to the limited number of stocks in some international markets\\
	
	Small Minus Big ala Hou et al & smb\_hxz\mbox{*} & Average of small portfolios minus average of large portfolios from roe\mbox{*} and inv\mbox{*}\\
		
	Market Volatility for Each Stock & \_mktvol\_zd\mbox{*} & 
	    $\sigma_{zD}(MKTRF\mbox{*}_t)$ \footnote{Must have enough non-missing values of stock to be estimated} \\

\end{longtable}
}

\setlength\LTleft{0pt}
\setlength\LTright{0pt}
{\scriptsize
\renewcommand{\arraystretch}{2}
	\begin{longtable}{@{\extracolsep{\fill}}|m{5cm}|l|m{8cm}|@{}}
		\caption{Market Characteristics \label{market_char}}\\
	
	\hline
	Name & Abbreviation & Construction \\
	\hline
	\endfirsthead
	
	\hline
	Name & Abbreviation & Construction \\
	\hline
	\endhead
	
	\hline
	\endfoot
	
	\hline\hline
	\endlastfoot
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Market Based Size Measures}} \\
	\hline 	
	
	Market Equity & market\_equity & $  ME\mbox{*}_t$\\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Total Dividend Paid to Market Equity}} \\
	\hline 	
	
	Dividend to Price - 1 Month & div1m\_me & $\frac{DIV\_TOT\mbox{*}_t\times SHARES\mbox{*}_t}{ME\mbox{*}_t}$\\
	
	Dividend to Price - 3 Months & div3m\_me &$\frac{\sum_{n = 0}^2 DIV\_TOT\mbox{*}_{t - n}\times SHARES\mbox{*}_{t - n}}{ME\mbox{*}_t}$\\
	
	Dividend to Price - 6 Months & div6m\_me &$\frac{\sum_{n = 0}^5 DIV\_TOT\mbox{*}_{t - n}\times SHARES\mbox{*}_{t - n}}{ME\mbox{*}_t}$\\
	
	Dividend to Price - 12 Months & div12m\_me &$ \frac{\sum_{n = 0}^{11} DIV\_TOT\mbox{*}_{t - n}\times SHARES\mbox{*}_{t - n}}{ME\mbox{*}_t}$\\

	\hline 
	\multicolumn{3}{|c|}{\textbf{Special Dividend Paid to Market Equity}} \\
	\hline 	
	
	Special Dividend to Price - 1 Month & divspc1m\_me & $\frac{DIV\_SPC\mbox{*}_t\times SHARES\mbox{*}_t}{ME\mbox{*}_t}$\\

    Special Dividend to Price - 12 Month & divspc12m\_me & $\frac{\sum_{n = 0}^{11} DIV\_SPC\mbox{*}_{t-n}\times SHARES\mbox{*}_{t-n}}{ME\mbox{*}_t}$\\

	\hline 
	\multicolumn{3}{|c|}{\textbf{Change in Shares Outstanding}} \\
	\hline 	
	
	Change in Shares - 1 Month & chcsho\_1m & $\frac{SHARES\mbox{*}_t\times  ADJFCT\mbox{*}_t}{SHARES\mbox{*}_{t-1}\times ADJFCT\mbox{*}_{t-1}} - 1$\\
	
	Change in Shares - 3 Month & chcsho\_3m & $\frac{SHARES\mbox{*}_t\times ADJFCT\mbox{*}_t}{SHARES\mbox{*}_{t-3}\times ADJFCT\mbox{*}_{t-3}} - 1$\\
	
	Change in Shares - 6 Month & chcsho\_6m & $\frac{SHARES\mbox{*}_t\times ADJFCT\mbox{*}_t}{SHARES\mbox{*}_{t-6}\times ADJFCT\mbox{*}_{t-6}} - 1$\\
	
	Change in Shares - 12 Month & chcsho\_12m & $\frac{SHARES\mbox{*}_t\times ADJFCT\mbox{*}_t}{SHARES\mbox{*}_{t-12}\times ADJFCT\mbox{*}_{t-12}} - 1$\\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Net Equity Payout}} \\
	\hline 	
	
	Net Equity Payout - 1 Month & eqnpo\_1m & $log\left(\frac{RI\mbox{*}_t}{RI\mbox{*}_{t-1}}\right) - log\left(\frac{ME\mbox{*}_t}{ME\mbox{*}_{t-1}}\right)$\\
	
	Net Equity Payout - 3 Month & eqnpo\_3m & $log\left(\frac{RI\mbox{*}_t}{RI\mbox{*}_{t-3}}\right) - log\left(\frac{ME\mbox{*}_t}{ME\mbox{*}_{t-3}}\right)$\\	
	
	Net Equity Payout - 6 Month & eqnpo\_6m & $log\left(\frac{RI\mbox{*}_t}{RI\mbox{*}_{t-6}}\right) - log\left(\frac{ME\mbox{*}_t}{ME\mbox{*}_{t-6}}\right)$\\
	
	Net Equity Payout - 12 Month & eqnpo\_12m & $log\left(\frac{RI\mbox{*}_t}{RI\mbox{*}_{t-12}}\right) - log\left(\frac{ME\mbox{*}_t}{ME\mbox{*}_{t-12}}\right)$\\	

	\hline 
	\multicolumn{3}{|c|}{\textbf{Momentum/Reversal}} \\
	\hline 	
	
	Short Term Reversal & ret\_1\_0 &$\frac{RI\mbox{*}_{t}}{RI\mbox{*}_{t-1}} - 1$\\
	
	Momentum 0-2 Months & ret\_2\_0 &$\frac{RI\mbox{*}_{t}}{RI\mbox{*}_{t-2}} - 1$\\
	
	Momentum 0-3 Months & ret\_3\_0 &$ \frac{RI\mbox{*}_{t}}{RI\mbox{*}_{t-3}} - 1$\\
	
	Momentum 1-3 Months & ret\_3\_1 &$\frac{RI\mbox{*}_{t-1}}{RI\mbox{*}_{t-3}} - 1$\\
	
	Momentum 0-6 Months & ret\_6\_0 &$\frac{RI\mbox{*}_{t}}{RI\mbox{*}_{t-6}} - 1$\\
	
	Momentum 1-6 Months & ret\_6\_1 &$\frac{RI\mbox{*}_{t-1}}{RI\mbox{*}_{t-6}} - 1$\\
	
	Momentum 0-9 Months & ret\_9\_0 &$\frac{RI\mbox{*}_{t}}{RI\mbox{*}_{t-9}} - 1$\\
	
	Momentum 1-9 Months & ret\_9\_1 &$\frac{RI\mbox{*}_{t-1}}{RI\mbox{*}_{t-9}} - 1$\\
	
	Momentum 0-12 Months & ret\_12\_0 &$ \frac{RI\mbox{*}_{t}}{RI\mbox{*}_{t-12}} - 1$\\
	
	Momentum 1-12 Months & ret\_12\_1 &$\frac{RI\mbox{*}_{t-1}}{RI\mbox{*}_{t-12}} - 1$\\
	
	Momentum 7-12 Months & ret\_12\_7 &$\frac{RI\mbox{*}_{t-7}}{RI\mbox{*}_{t-12}} - 1$\\
	
	Momentum 1-18 Months & ret\_18\_1 &$\frac{RI\mbox{*}_{t-1}}{RI\mbox{*}_{t-18}} - 1$\\
	
	Momentum 1-24 Months & ret\_24\_1 &$\frac{RI\mbox{*}_{t-1}}{RI\mbox{*}_{t-24}} - 1$\\
	
	Momentum 12-24 Months & ret\_24\_12 &$\frac{RI\mbox{*}_{t-12}}{RI\mbox{*}_{t-24}} - 1$\\
	
	Momentum 1-36 Months & ret\_36\_1 &$\frac{RI\mbox{*}_{t-1}}{RI\mbox{*}_{t-36}} - 1$\\
	
	Momentum 12-36 Months & ret\_36\_12 &$\frac{RI\mbox{*}_{t-12}}{RI\mbox{*}_{t-36}} - 1$\\
	
	Momentum 1-48 Months & ret\_48\_1 &$\frac{RI\mbox{*}_{t-1}}{RI\mbox{*}_{t-48}} - 1$\\
	
	Momentum 12-48 Months & ret\_48\_12 &$\frac{RI\mbox{*}_{t-12}}{RI\mbox{*}_{t-48}} - 1$\\
	
	Momentum 1-60 Months & ret\_60\_1 &$\frac{RI\mbox{*}_{t-1}}{RI\mbox{*}_{t-60}} - 1$\\
	
	Momentum 12-60 Months & ret\_60\_12 &$\frac{RI\mbox{*}_{t-12}}{RI\mbox{*}_{t-60}} - 1$\\
	
	Momentum 36-60 Months & ret\_60\_36 &$\frac{RI\mbox{*}_{t-36}}{RI\mbox{*}_{t-60}} - 1$\\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Seasonality}} \\
	\hline 	
		
	1 Year Annual Seasonality & seas\_1\_1an & Return in month t-12 \\
		
	2 - 5 Year Annual Seasonality & seas\_2\_5an & Average return over annual lags from year t-2 to t-5 \\
		
	6 - 10 Year Annual Seasonality & seas\_6\_10an &Average return over annual lags from year t-6 to t-10 \\
		
	11 - 15 Year Annual Seasonality & seas\_11\_15an & Average return over annual lags from year t-11 to t-15 \\
		
	16 - 20 Year Annual Seasonality & seas\_16\_20an & Average return over annual lags from year t-16 to t-20) \\
		
	1 Year Non-Annual Seasonality & seas\_1\_1na & Average return from month t-1 to t-11 \\
		
	2 - 5 Year Non-Annual Seasonality & seas\_2\_5na & Average return over non-annual lags from year t-2 to t-5 \\
		
	6 - 10 Year Non-Annual Seasonality & seas\_6\_10na & Average return over non-annual lags from year t-6 to t-10 \\
		
	11 - 15 Year Non-Annual Seasonality & seas\_11\_15na & Average return over non-annual lags from year t-11 to t-15 \\
		
	16 - 20 Year Non-Annual Seasonality & seas\_16\_20na & Average return over non-annual lags from year t-16 to t-20 \\
	
	\hline 
	\multicolumn{3}{|c|}{\textbf{Combined Accounting and Market Based Characteristics}} \\
	\hline 	
	
	\multicolumn{3}{|c|}{Let $e_t$ be defined as described \hyperlink{e_ff3}{here}}\\
	
	\hline
	
	60 Month CAPM Beta & beta\_60m & $\frac{COVAR\_60M(RET\mbox{*}_t, MKTRF\mbox{*}_t)}{VARC\_60M(MKTRF\mbox{*}_t)}$ \\
	
	Performance Based Mispricing & mispricing\_perf\footnote{A rank characteristic has the value of that characteristics rank with respect to other companies' same characteristic of the same month and country scaled [0, 1]. This is identified with a ``r01" superscript.} &
		
	$
	\begin{aligned}
		\frac{1}{4}\big(&O\_SCORE^{r01}_t + RET\_12\_1^{r01}_t + \\ &GP\_AT^{r01}_t + NIQ\_AT^{r01}_t\big)
		\\ &
	\end{aligned} 
		$ 
		%\begin{multline*}
		%       \frac{1}{4}(O\_SCORE^{r01}_t + RET\_12\_1^{r01}_t + \\ GP\_AT^{r01}_t + NIQ\_AT^{r01}_t)
		%\end{multline*} 
	\\
	
	Management Based Mispricing & mispricing\_mgmt & 
	$
	\begin{aligned}
		\frac{1}{6}\big(&CHCSHO\_12M^{r01}_t + EQNPO\_12M^{r01}_t + \\ 
		&OACCRUALS\_AT^{r01}_t +  NOA\_AT^{r01}_t + \\
		&AT\_GR1^{r01}_t +  PPEINV\_GR1A^{r01}_t\big)
	\end{aligned} 
	$
		
		%\begin{multline*}
		%    \frac{1}{6}(CHCSHO\_12M^{r01}_t + EQNPO\_12M^{r01}_t + \\ 
		%    OACCRUALS\_AT^{r01}_t +  NOA\_AT^{r01}_t + \\
		%    AT\_GR1^{r01}_t +  PPEINV\_GR1A^{r01}_t)
		%\end{multline*} 
	\\
	
	Residual Momentum - 6 Month & resff3\_6\_1 & $ -1 + \prod_{n = 1}^6 1 + e_{t-n}$ \\
	
	Residual Momentum - 12 Month & resff3\_12\_1 & $-1 + \prod_{n = 1}^{12} 1 + e_{t-n}$\\
	
	\hline
	\multicolumn{3}{|c|}{\textbf{\hypertarget{factors2}{Daily Market Data}\footnote{{Many of the variables in this section are estimated using rolling windows of data, and the variables are estimated using a variety of window lengths: 21, 126, 252 and 1260 days. In this section, I refer to the number of days as m as a proxy for any of the possible window lengths.}}}} \\
	\hline
	
	\multicolumn{3}{|c|}{Let $\epsilon_t$ be defined as described \hyperlink{ep_capm}{here}}\\

    \hline
	
	Return Volatility & rvol\_zd & $\sigma_{zD}(RET\_EXC\mbox{*}_t)$\\
	
	Maximum Return & rmax1\_zd &$MAX1\_zD(RET\mbox{*}_t)$\\
	
	Mean Maximum Return & rmax5\_zd &$\frac{1}{5}\sum_{n = 1}^5 X_n, \;\; X_n \in MAX5\_zD(RET\mbox{*})$ \\
	
	Return Skewness & rskew\_zd & $ SKEW\_zD(RET\_EXC\mbox{*}_t)$\\
    
    Price-to-High & prc\_highprc\_zd & $\frac{PRC\_ADJ\mbox{*}_t}{MAX1\_zD(PRC\_ADJ\mbox{*}_t)}$\\
    
    Amihud (2002) Measure & ami\_zd &$\overline{\left(\frac{|RET\mbox{*}_t|}{DOLVOL\mbox{*}_t}\right)}_{zD}*1000000$ \\
    
    CAPM Beta & beta\_zd & Described in detail \hyperlink{factors}{here} \\
    
    CAPM Idiosyncratic Vol. & ivol\_capm\_zd & Described in detail \hyperlink{factors}{here}\\
    
    CAPM Skewness & iskew\_capm\_zd & Described in detail \hyperlink{factors}{here} \\

    Coskewness & coskew\_zd\footnote{$MKTRF\_DM_t = MKTRF\mbox{*}_t - \overline{MKTRF\mbox{*}_t}_{zD}$} &$\frac{\overline{(\epsilon_t \times MKTRF\_DM_t^2)}_{zD}}{\sqrt{\overline{(\epsilon_t^2)}_{zD} \times \overline{(MKTRF\_DM_t^2)}_{zD}}}$\\
    
    Fama and French Idiosyncratic Vol. & ivol\_ff3\_zd & Described in detail \hyperlink{factors}{here}\\ 
     
    Fama and French Skewness & iskew\_ff3\_zd & Described in detail \hyperlink{factors}{here} \\   
    
    Hou, Xue and Zhang Idiosyncratic Vol. & ivol\_hxz4\_zd & Described in detail \hyperlink{factors}{here}\\ 
     
    Hou, Xue and Zhang Skewness & iskew\_hxz4\_zd & Described in detail \hyperlink{factors}{here} \\    
    
    Dimson Beta & beta\_dimson\_zd & Created as described in Dimson (1979) \\
    
    \hypertarget{dbeta2}{Downside Beta} & betadown\_zd & Described in detail \hyperlink{dbeta}{here} \\
    
	Zero Trades & zero\_trades\_zd & Number of days with zero trades over period. In case of equal number of zero trading days, turnover\_zd will decide on the rank following Liu (2006) \\
    
    Turnover & turnover\_zd &$\overline{\left(\frac{TVOL\mbox{*}_t}{SHARES\mbox{*}_t*1000000}\right)}_{zD}$\\
    
    Turnover Volatility & turnover\_var\_zd & $\frac{\sigma_{zD}\left((TVOL\mbox{*}_t/SHARES\mbox{*}_t)*1000000\right)}{TURNOVER\_zD_t}$\\
    
    Dollar Volume & dolvol\_zd &$\overline{DOLVOL\mbox{*}_t}_{zD}$\\
    
    Dollar Volume Volatility & dolvol\_var\_zd & $\frac{\sigma_{zD}(DOLVOL\mbox{*}_t)}{DOLVOL\_zD_t}$ \\
    
    Correlation to Market & corr\_zd & The correlation between $RET\_EXC\mbox{*}_3l = RET\_EXC\mbox{*}_t + RET\_EXC\mbox{*}_{t-1} + RET\_EXC\mbox{*}_{t-2}$ and $MKT\_EXC\_3l = MKTRF\mbox{*}_t + MKTRF\mbox{*}_{t-1} + MKTRF\mbox{*}_{t-2}$ \\
    
    Betting Against Beta & betabab\_1260d & $\frac{CORR\_1260d_t \times RVOL\_252d_t}{\_MKTVOL\_252d\mbox{*}_t}$ \\
    
    Max Return to Volatility & rmax5\_rvol\_21d &$\frac{RMAX5\_21d_t}{RVOL\_252d_t}$ \\
    
	21 Day Bid-Ask High-Low & bidaskhl\_21d &
	High-low bid ask estimator created using code from Corwin and Schultz (2012) \\
	
	21 Day Return Volatility High-Low & rvolhl\_21d & High-low return volatility estimator created using code from Corwin and Schultz (2012) \\
	
	\hline
	\multicolumn{3}{|c|}{\textbf{Quality Minus Junk}} \\
	\hline 	
	
		Quality Minus Junk - Profit & qmj\_prof & 
		%\begin{equation*}
		$
		\begin{aligned}
			ZV\Big( &ZV(GP\_AT_t) + ZV(NI\_BE_t) + \\ &ZV(NI\_AT_t) + ZV(OCF\_AT_t) 
			+ ZV(GP\_SALE\mbox{*}_t) + \\    &ZV(OACCRUALS\_AT_t)\Big) 
			\\ &
		\end{aligned} 
		$
		%\end{equation*} 
		\\
		
		Quality Minus Junk - Growth & qmj\_growth & 
		%\begin{equation*}
		$
		\begin{aligned}
			ZV\Big( &ZV(GPOA\_CH5_t) + ZV(ROE\_CH5_t) \\ + &ZV(ROA\_CH5_t) + ZV(CFOA\_CH5_t) + \\ &ZV(GMAR\_CH5_t) \Big)
			\\ &
		\end{aligned} 
		$
		%\end{equation*} 
		\\
		
		
		Quality Minus Junk - Safety & qmj\_safety & 
		%\begin{equation*}
		$
		\begin{aligned}
			ZV\Big( &ZV(BETABAB\_1260d_t) + ZV(DEBT\_AT_t) \\ + &ZV(O\_SCORE_t) + ZV(Z\_SCORE_t) + ZV(\_EVOL_t)\Big)
			%\\ &
		\end{aligned} 
		$
		%\end{equation*} 
		\\
	
	Quality Minus Junk & qmj & $\frac{QMJ\_PROF_t + QMJ\_GROWTH_t + QMJ\_SAFETY_t}{3}$
\end{longtable}
}
    
\begin{section}{Detailed Characteristic Construction}
    This section includes detailed descriptions how we built characteristics that don't easily fit into the Accounting Characteristics or Market Characteristics tables. 
    \begin{itemize}
        \item \hyperlink{eq_dur2}{\hypertarget{eq_dur}{Equity Duration}}
            \begin{itemize}
                \item Define the following variables:
                \begin{itemize}
                    \item horizon: number of months used to estimate helper variables
                    \item r: constant used as assumed discount rate
                    \item roe\_mean: constant used as the average ROE value
                    \item roe\_ar1: constant used as the expected growth rate of ROE
                    \item g\_mean: constant used as the average sales growth rate
                    \item g\_ar1: constant used as the expected growth rate of sales
                \end{itemize}
                \item Create initial variables:   
                    \begin{align*}
                        \_roe0 &= \frac{NI\mbox{*}_t}{BE\mbox{*}_{t-12}} \\
                        \_g0 &= \frac{SALE\mbox{*}_t}{SALE\mbox{*}_{t-12}} - 1 \\
                        \_be0 &= BE\mbox{*}_t
                    \end{align*}
                    \begin{itemize}
                        \item If the number of non-missing observations is less than or equal to 12 or the variables' respective denominators are less than or equal to 1 $\_roe0_t$ and $\_g0_t$ are set to missing. 
                    \end{itemize}
                
                \item Forecast cash distributions
                    \begin{align*}
                        roe\_c &= roe\_mean \times (1 - roe\_ar1) \\
                        g\_c &= g\_mean \times (1 - g\_ar1) \\
                        \_roe_t &= \sum_{i = 1}^{horizon} roe\_c + roe\_ar1 \times \_roe_{t-i} \\
                        \_g_t &= \sum_{i = 1}^{horizon} g\_c + g\_ar1 \times \_g_{t-i} \\
                        \_be_t& = \sum_{i = 1}^{horizon} \_be_{t-i} \times (1 + \_g_t) \\
                        \_cd_t &= \sum_{i = 1}^{horizon} \_be_t \times (\_roe_t - \_g_t)
                    \end{align*}

                \item Create duration helper variables \footnote{ $ed\_cw\_w$, $ed\_cd$ and $ed\_err$ are equal to 0 at i = 1. $ed\_cw\_w$ and $ed\_cd$ recusrively build upon themselves over the length of the horiozon, so $ed\_cw\_w_{i-1}$, for example, would be the previous iteration of $ed\_cw\_w$}
                    
                    \begin{align*}
                        ed\_constant &= horizon + \frac{1 + r}{r} \\
                        ed\_cw\_w_t &= \sum_{i = 1}^{horizon} ed\_cd\_w_{i - 1} + i \times \frac{\_\_cd_t}{(1 + r)^i} \\ 
                        ed\_cd_t &= \sum_{i = 1}^{horizon} ed\_cd_{i - 1} + \frac{\_\_cd_t}{(1 + r)^i}
                    \end{align*}

                \item Characteristic:
                    \begin{equation*}
                        eq\_dur_t = \frac{ed\_ed\_w_t \times FX_t}{ME\_COMPANY_t} + ed\_constant \times \frac{ME\_COMPANY_t - ed\_cd_t \times FX_t}{ME\_COMPANY_t}
                    \end{equation*}
            \end{itemize}
            
        \item \hyperlink{pio2}{\hypertarget{pio}{Piotroski F-Score}}
            \begin{itemize}
                \item Create helper variables: 
                    \begin{align*}
                        \_f\_roa_t &= \frac{NI\mbox{*}_t}{AT\mbox{*}_{t-12}} \\
                        \_f\_croa_t &= \frac{OCF\mbox{*}_t}{AT\mbox{*}_{t-12}} \\
                        \_f\_droa_t &= \_f_\_roa_t - \_f\_roa_{t-12} \\
                        \_f\_acc_t &= \_f\_croa_t - \_f\_roa_t \\
                        \_f\_lev &= \frac{DLTT_t}{AT\mbox{*}_t} - \frac{DLTT_{t-12}}{AT\mbox{*}_{t-12}} \\
                        \_f\_liq_t &= \frac{CA\mbox{*}_t}{CL\mbox{*}_t} - \frac{CA\mbox{*}_{t-12}}{CL\mbox{*}_{t-12}} \\
                        \_f\_eqis_t &= EQIS\mbox{*}_t \\
                        \_f\_gm_t &= \frac{GP\mbox{*}_t}{SALE\mbox{*}_t} - \frac{GP\mbox{*}_{t-12}}{SALE\mbox{*}_{t-12}} \\
                        \_f\_aturn_t &= \frac{SALE\mbox{*}_t}{AT\mbox{*}_{t-12}} - \frac{SALE\mbox{*}_{t-12}}{AT\mbox{*}_{t-24}} 
                    \end{align*}
                    
                    \begin{itemize}
                        \item For all variables except $\_f\_acc$, $\_f\_aturn$ $\_f\_eqis$, if the count of available observations is less than or equal to 12, then the variable is set to missing. If $\_f\_aturn$ has less than or equal to 24 non-missing observations, it is set to missing. If a variable has $AT\mbox{*}_t$ or $AT\mbox{*}_{t-12}$ as an input and $AT\mbox{*}_t \leq 0$ or $AT\mbox{*}_{t-12} \leq 0$, then it is set to missing. If $CL\mbox{*}_t \leq 0$ or $CL\mbox{*}_{t-12} \leq 0$ then $\_f\_liq_t$ is set to missing. If $SALE\mbox{*}_t \leq 0$ or $SALE\mbox{*}_{t-12} \leq 0$ then $\_f\_gm_t$ is set to missing.
                    \end{itemize}
                    
                \item Characteristic\footnote{A subscript of $ > 0$, ex: ${VAR_t}_{>0, t}$, is a dummy for if the variable is greater than zero, and it is defined similarly for ${VAR_t}_{<0, t}$ or any other specification. Otherwise, not included as an input, Also, if any variables other than \_f\_eqis$_t$ are missing, then f\_score$_t$ is set to missing.} 
                    \begin{align*}
                        f\_score_t =& \_f\_roa_{>0, t} + \_f\_croa_{>0, t} + \_f\_droa_{>0, t} + \_f\_acc_{>0, t} + \\ &\_f\_lev_{<0, t} + \_f\_liq_{>0, t} + \_f\_eqis_{=0, t} + \_f\_gm_{>0, t} + \_f\_aturn_{>0, t}
                    \end{align*}
            \end{itemize}
        
        \item \hyperlink{ohl2}{\hypertarget{ohl}{Ohlson O-Score}}
            \begin{itemize}
                \item Create helper variables:
                \begin{align*}
                    \_o\_lat_t &= AT\mbox{*}_{t-1} \\
                    \_o\_lev_t &= \frac{DEBT\mbox{*}_t}{AT\mbox{*}_t} \\
                    \_o\_wc_t &= \frac{CA\mbox{*}_t - CL\mbox{*}_t}{AT\mbox{*}_t}  \\
                    \_o\_roe_t &= \frac{NIX\mbox{*}_t}{AT\mbox{*}_t} \\
                    \_o\_cacl_t &= \frac{CL\mbox{*}_t}{CA\mbox{*}_t} \\
                    \_o\_ffo_t &= \frac{PI\mbox{*}_t + DP_t}{LT_t} \\
                    \_o\_neg\_eq_t &= 1 \text{ if } LT_t > AT\mbox{*}_t, \text{ otherwise } 0 \\
                    \_o\_neg\_earn &= 1 \text{ if } NIX\mbox{*}_t < 0 \text{ and } NIX\mbox{*}_{t-12} < 0 \\
                    \_o\_nich_t &= \frac{NIX\mbox{*}_t - NIX\mbox{*}_{t-12}}{|NIX\mbox{*}_t| +  |NIX\mbox{*}_{t-12}|} 
            \end{align*}
            
                \begin{itemize}
                    \item If $AT\mbox{*}_t \leq 0$, then $\_o\_lat_t$, $\_o\_lev_t$, $\_o\_wc_t$, and $\_o\_roe_t$ are set to missing. If $CA\mbox{*}_t \leq 0$ then $\_o\_cacl_t$ is set to missing. If $LT_T \leq 0$ then $\_o\_ffo_t$ is set to missing. If $LT_t$ or $AT\mbox{*}_t$ are missing, then $\_o\_neg\_eq_t$ is set to missing. If there are less than or equal to 12 observations or either of $NIX\mbox{*}_t$ and $NIX\mbox{*}_{t-12}$ are missing, then $\_o\_nich_t$ and $\_o\_neg\_earn_t$ are set to missing.
                \end{itemize}
            
                \item Characteristic:
                \begin{align*}
                    o\_score_t =& -1.37 - 0.407 \times \_o\_lat_t + 6.03 \times \_o\_lev_t + 1.43 \times \_o\_wc_t + \\ &0.076 \times \_o\_cacl_t - 1.72 \times \_o\_neg\_eq_t - 2.37 \times \_o\_roe_t - \\ &1.83 \times \_o\_ffo_t + 0.285 \times \_o\_neg\_earn_t - 0.52 \times \_o\_nich_t
                \end{align*}
            \end{itemize}
            
        \item \hyperlink{alt2}{\hypertarget{alt}{Altman Z-Score}}
            \begin{itemize}
                \item Create helper variables:
                    \begin{align*}
                        \_z\_wc_t &= \frac{CA\mbox{*}_t - CL\mbox{*}_t}{AT\mbox{*}_t} \\
                        \_z\_re_t &= \frac{RE_t}{AT\mbox{*}_t} \\
                        \_z\_eb_t &= \frac{EBITDA\mbox{*}_t}{AT\mbox{*}_t} \\
                        \_z\_sa_t &= \frac{SALE\mbox{*}_t}{AT\mbox{*}_t} \\
                        \_z\_me_t &= \frac{ME\_FISCAL_t}{LT_t}
                    \end{align*}
                
                    \begin{itemize}
                        \item If $AT\mbox{*}_t \leq 0$ then any variable including $AT\mbox{*}_t$, then it is set to missing. If $LT_t \leq 0$, then $\_z\_me_t$ is set to missing. 
                    \end{itemize}
                
                \item Characteristic: 
                    \begin{equation*}
                        z\_score_t = 1.2 \times \_z\_wc_t + 1.4 \times \_z\_re_t + 3.3 \times \_z\_eb_t + 0.6 \times \_z\_me_t + 1.0 \times \_z\_sa_t
                    \end{equation*}
            \end{itemize}

        \item \hyperlink{kap2}{\hypertarget{kap}{Kaplan-Zingales Index}}
            \begin{itemize}
                \item Create helper variables:
                    \begin{align*}
                        \_kz\_cf_t &= \frac{NI\mbox{*}_t + DP_t}{PPENT_{t-12}} \\
                        \_kz\_q_t &= \frac{AT\mbox{*}_t + ME\_FISCAL_t - BE\mbox{*}_t}{AT\mbox{*}_t} \\
                        \_kz\_db_t &= \frac{DEBT\mbox{*}_t}{DEBT\mbox{*}_t + SEQ\mbox{*}_t} \\
                        \_kz\_dv_t &= \frac{DIV\mbox{*}_t}{PPENT_{t-12}} \\
                        \_kz\_cs_t &= \frac{CHE_t}{PPENT_{t-12}}
                    \end{align*}
                    \begin{itemize}
                        \item If the number of non-missing observations is less than or equal to 12, then $\_kz\_cf_t$, $\_kz\_dv_t$ and $\_kz\_cs_t$ are set to zero. If $PPENT_{t-12} \leq 0$ then $\_kz\_cf_t$, $\_kz\_dv_t$ and $\_kz\_cs_t$ are set to missing. If $AT\mbox{*}_t \leq 0$ then $\_kz\_q_t$ is set to missing. If $(DEBT\mbox{*}_t + SEQ\mbox{*}_t) = 0$ then $\_kz\_db_t$ is set to missing.
                    \end{itemize}
                
                \item Characteristic:
                    \begin{equation*}
                        kz\_index = -1.002 \times \_kz\_cf_t \:+\: 0.283 \times \_kz\_q_t \:+\: 3.139 \times \_kz\_db_t \:-\: 39.368 \times \_kz\_dv_t \:-\: 1.315 \times \_kz\_cs_t
                    \end{equation*}
            \end{itemize}
            
        \item \hyperlink{intval2}{\hypertarget{intval}{Intrinsic Value from Frankel and Lee}}
            \begin{itemize}
                \item Define $r$ as a constant assumed discount rate
                \item Create helper variables:
                    \begin{align*}
                        \_iv\_po_t &= \frac{DIV\mbox{*}_t}{NIX\mbox{*}_t} \\
                        \_iv\_roe_t &= \frac{NIX\mbox{*}_t}{(BE\mbox{*}_t + BE\mbox{*}_{t-12})/2} \\
                        \_iv\_be1_t &= (1 + (1 - \_iv\_po_t) \times \_iv\_roe_t) \times BE\mbox{*}_t)
                    \end{align*}
                    \begin{itemize}
                        \item If $NIX\mbox{*}_t \leq 0$ then 
                            \begin{equation*}
                                \_iv\_po_t = \frac{DIV\mbox{*}_t}{AT\mbox{*}_t \times 0.06}
                            \end{equation*}
                        \item If the number of non-missing observations is less than or equal to 12 or $(BE\mbox{*}_t + BE\mbox{*}_{t-12}) \leq 0$ then $\_iv\_roe_t$ is set to missing. 
                    \end{itemize}
                    
                \item Characteristics: 
                    \begin{equation*}
                        intrinsic\_value_t = BE\mbox{*}_t + \frac{\_iv\_roe_t - r}{1 + r} \times BE\mbox{*}_t + \frac{\_iv\_roe_t - r}{(1 + r)\times r} \times \_iv\_be1_t
                    \end{equation*}
                    \begin{itemize}
                        \item If $intrinsic\_value_t \leq 0$ then it is set to missing.
                    \end{itemize}
            \end{itemize}
            
        \item \hyperlink{ni_ivol2}{\hypertarget{ni_ivol}{Net Income Idiosyncratic Volatility}}
            \begin{itemize}
                \item Define the following variable \footnote{If $AT\mbox{*}_t\leq 0$, then $\_ni\_at_t$ is set to missing}:
                        \begin{equation*}
                            \_ni\_at_t = \frac{NI\mbox{*}_t}{AT\mbox{*}_t}
                        \end{equation*}
                    
                \item A rolling regression of the following form is run for each company, with the time series split up into n groups:  
                        \begin{equation*} 
                            \_ni\_at_{t} = \beta_0 + \beta_1\_ni\_at_{t - 12} + u_t 
                        \end{equation*}
                        where $edf_{t}$ = the error degrees of freedom of regression and $rmse_{t}$ = root mean square error of the regression.
                    
                \item Characteristic:
                    \begin{equation*}
                        ni\_ivol_t = \sqrt{\frac{rmse_t^2 \times edf_t}{edf_t + 1}}
                    \end{equation*}
            \end{itemize}
            
        \item \hyperlink{factors2}{\hypertarget{factors}{Beta, Idiosyncratic Volatility and Skewness of Asset Pricing Factor Regressions}}
            \begin{itemize}
                \item This section describes the construction of beta\_zd for the CAPM model, and the idiosyncratic volatility and skewness characteristics, which are estimated using three different factor models:
                    \begin{itemize}
                        \item \hypertarget{ep_capm}{CAPM (capm)}:
                        \begin{equation*}
                            RET\_EXC\mbox{*}_t = \beta_0 + \beta_1 MKTRF\mbox{*}_t + \epsilon_t
                        \end{equation*}
                        
                        \item \hypertarget{e_ff3}{Fama-French 3 Factor Model (ff3)}:
                        \begin{equation*}
                            RET\_EXC\mbox{*}_t = \beta_0 + \beta_1 MKTRF\mbox{*}_t + \beta_2 HML\mbox{*}_t + \beta_3 SMB\_FF\mbox{*}_t + e_t
                        \end{equation*}
                        
                        \item Hou, Xue and Zhang 4 Factor Model (hxz4):
                        \begin{equation*}
                            RET\_EXC\mbox{*}_t = \beta_0 + \beta_1 MKTRF\mbox{*}_t + \beta_2 SMB\_HXZ\mbox{*}_t + \beta_3 ROE\mbox{*}_t + \beta_4 INV\mbox{*}_t + \mu_t
                        \end{equation*}
                    \end{itemize}

                \item Characteristics \footnote{$z$ indicates over how many days the model is run.}:
                    \begin{align*}
                        beta\_zd &= \beta_1 \text{ from the CAPM model} \\
                        ivol\_capm\_zd_t &= \sigma_{zD}(\epsilon_t) \\
                        ivol\_ff3\_zd_t &= \sigma_{zD}(e_t) \\
                        ivol\_hxz4\_zd_t &= \sigma_{zD}(\mu_t) \\
                        iskew\_capm\_zd_t &= SKEW\_zD(\epsilon_t) \\
                        iskew\_ff3\_zd_t &= SKEW\_zD(e_t) \\
                        iskew\_hxz4\_zd_t &= SKEW\_zD(\sigma_t) \\
                    \end{align*}
            \end{itemize}
            
        \item \hyperlink{dbeta2}{\hypertarget{dbeta}{Downside Beta}}
            \begin{itemize}
                \item Define the following regression model run over z days:
                    \begin{equation*}
                        RET\_EXC\mbox{*}_t = \beta_0 + \beta_1 MKTRF\mbox{*}_t + \epsilon_t
                    \end{equation*}
                    However, we restrict the data to when $MKTRF\mbox{*}$ is negative.
                \item Characteristic:
                    \begin{itemize}
                        \item $betadown\_zd = \beta_1$
                    \end{itemize}
            \end{itemize}
            
    \end{itemize}

\end{section}

\begin{section}{FX Conversion Rate Construction}
This section outlines how we create a daily dataset, beginning 01/01/1950 to now, of X currency - USD exchange rate using COMPUSTAT. This is run in the macro $compustat\_fx()$ in the $project\_macros.sas$ file.
    \begin{itemize}
        \item We use COMP.EXRT\_DLY, which has daily conversion rates from GBP to other currencies 'X'. 
        \item Every day available, we estimate the exchange rate $fx_t$ as 
            \begin{equation*}
                fx_t = \frac{USD_{GBP, t}}{X_{GBP, t}}
            \end{equation*}
            where $X_{GBP,t}$ is the exchange rate of GBP to currency X on day $t$. 
        \item In case there are gaps in information, we assume the exchange rate of the last observation until a new observation is available. 
        \item $fx_t$ is quoted as $\frac{X_t}{USD_t}$ , so to go from X to USD, do $X_t \times fx_t$
    \end{itemize}

\end{section}

\section{Factor Details and Citations}

\begingroup\fontsize{9pt}{12pt}\selectfont
%\renewcommand{\arraystretch}{1.4}
\begin{longtable}{p{5cm}p{2cm}p{5cm}lll}
        \caption{Factor and Cluster Details} \label{tbl:factor:details}\\
        \hline
         & Variable &  & Orig. &  & Orig. \\
        Description & Name & Citation & Sample & Sign & Signif. \\
        \hline
        \\[-2ex]
\multicolumn{6}{c}{\underline{\bf Accruals}} \\
Change in current operating working capital & cowc\_gr1a & \citeA{richardson2005} & 1962-2001 & -1 & 1 \\
Operating accruals & oaccruals\_at & \citeA{sloan1996} & 1962-1991 & -1 & 1 \\
Percent operating accruals & oaccruals\_ni & \citeA{hafzalla2011} & 1989-2008 & -1 & 1 \\
Years 16-20 lagged returns, nonannual & seas\_16\_20na & \citeA{heston2008} & 1965-2002 & 1 & 1 \\
Total accruals & taccruals\_at & \citeA{richardson2005} & 1962-2001 & -1 & 1 \\
Percent total accruals & taccruals\_ni & \citeA{hafzalla2011} & 1989-2008 & -1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Debt Issuance}} \\
Abnormal corporate investment & capex\_abn & \citeA{titman2004} & 1973-1996 & -1 & 1 \\
Growth in book debt (3 years) & debt\_gr3 & \citeA{lyandres2008} & 1970-2005 & -1 & 1 \\
Change in financial liabilities & fnl\_gr1a & \citeA{richardson2005} & 1962-2001 & -1 & 1 \\
Change in noncurrent operating liabilities & ncol\_gr1a & \citeA{richardson2005} & 1962-2001 & -1 & 0 \\
Change in net financial assets & nfna\_gr1a & \citeA{richardson2005} & 1962-2001 & 1 & 1 \\
Earnings persistence & ni\_ar1 & \citeA{francis2004} & 1975-2001 & 1 & 0 \\
Net operating assets & noa\_at & \citeA{hirshleifer2004} & 1964-2002 & -1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Investment}} \\
Liquidity of book assets & aliq\_at & \citeA{ortiz2014} & 1984-2006 & -1 & 0 \\
Asset Growth & at\_gr1 & \citeA{cooper2008} & 1968-2003 & -1 & 1 \\
Change in common equity & be\_gr1a & \citeA{richardson2005} & 1962-2001 & -1 & 1 \\
CAPEX growth (1 year) & capx\_gr1 & \citeA{xie2001} & 1971-1992 & -1 & 0 \\
CAPEX growth (2 years) & capx\_gr2 & \citeA{anderson2006} & 1976-1998 & -1 & 1 \\
CAPEX growth (3 years) & capx\_gr3 & \citeA{anderson2006} & 1976-1998 & -1 & 1 \\
Change in current operating assets & coa\_gr1a & \citeA{richardson2005} & 1962-2001 & -1 & 1 \\
Change in current operating liabilities & col\_gr1a & \citeA{richardson2005} & 1962-2001 & -1 & 1 \\
Hiring rate & emp\_gr1 & \citeA{belobaz2014} & 1965-2010 & -1 & 1 \\
Inventory growth & inv\_gr1 & \citeA{belo2012} & 1965-2009 & -1 & 1 \\
Inventory change & inv\_gr1a & \citeA{thomas2002} & 1970-1997 & -1 & 1 \\
Change in long-term net operating assets & lnoa\_gr1a & \citeA{fairfield2003} & 1964-1993 & -1 & 1 \\
Mispricing factor: Management & mispricing\_mgmt & \citeA{stambaugh2017} & 1967-2013 & 1 & 1 \\
Change in noncurrent operating assets & ncoa\_gr1a & \citeA{richardson2005} & 1962-2001 & -1 & 1 \\
Change in net noncurrent operating assets & nncoa\_gr1a & \citeA{richardson2005} & 1962-2001 & -1 & 1 \\
Change in net operating assets & noa\_gr1a & \citeA{hirshleifer2004} & 1964-2002 & -1 & 1 \\
Change PPE and Inventory & ppeinv\_gr1a & \citeA{lyandres2008} & 1970-2005 & -1 & 1 \\
Long-term reversal & ret\_60\_12 & \citeA{de1985} & 1926-1982 & -1 & 1 \\
Sales Growth (1 year) & sale\_gr1 & \citeA{lakonishok1994} & 1968-1989 & -1 & 1 \\
Sales Growth (3 years) & sale\_gr3 & \citeA{lakonishok1994} & 1968-1989 & -1 & 1 \\
Sales growth (1 quarter) & saleq\_gr1 &   & 1967-2016 & -1 & 0 \\
Years 2-5 lagged returns, nonannual & seas\_2\_5na & \citeA{heston2008} & 1965-2002 & -1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Low Leverage}} \\
Firm age & age & \citeA{jiang2005} & 1965-2001 & -1 & 1 \\
Liquidity of market assets & aliq\_mat & \citeA{ortiz2014} & 1984-2006 & -1 & 0 \\
Book leverage & at\_be & \citeA{fama1992} & 1963-1990 & -1 & 0 \\
The high-low bid-ask spread & bidaskhl\_21d & \citeA{corwin2012} & 1927-2006 & 1 & 1 \\
Cash-to-assets & cash\_at & \citeA{palazzo2012} & 1972-2009 & 1 & 0 \\
Net debt-to-price & netdebt\_me & \citeA{penman2007} & 1962-2001 & -1 & 1 \\
Earnings volatility & ni\_ivol & \citeA{francis2004} & 1975-2001 & 1 & 0 \\
R\&D-to-sales & rd\_sale & \citeA{chan2001} & 1975-1995 & 1 & 0 \\
R\&D capital-to-book assets & rd5\_at & \citeA{li2011} & 1952-2004 & 1 & 0 \\
Asset tangibility & tangibility & \citeA{hahn2009} & 1973-2001 & 1 & 0 \\
Altman Z-score & z\_score & \citeA{dichev1998} & 1981-1995 & 1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Low Risk}} \\
Market Beta & beta\_60m & \citeA{fama1973} & 1935-1968 & -1 & 1 \\
Dimson beta & beta\_dimson\_21d & \citeA{dimson1979} & 1955-1974 & -1 & 0 \\
Frazzini-Pedersen market beta & betabab\_1260d & \citeA{frazzini2014} & 1926-2012 & -1 & 1 \\
Downside beta & betadown\_252d & \citeA{angchen2006} & 1963-2001 & -1 & 1 \\
Earnings variability & earnings\_variability & \citeA{francis2004} & 1975-2001 & -1 & 0 \\
Idiosyncratic volatility from the CAPM (21 days) & ivol\_capm\_21d &   & 1967-2016 & -1 & 0 \\
Idiosyncratic volatility from the CAPM (252 days) & ivol\_capm\_252d & \citeA{ali2003} & 1976-1997 & -1 & 1 \\
Idiosyncratic volatility from the Fama-French 3-factor model & ivol\_ff3\_21d & \citeA{anghod2006} & 1963-2000 & -1 & 1 \\
Idiosyncratic volatility from the q-factor model & ivol\_hxz4\_21d &   & 1967-2016 & -1 & 0 \\
Cash flow volatility & ocfq\_saleq\_std & \citeA{huang2009} & 1980-2004 & -1 & 1 \\
Maximum daily return & rmax1\_21d & \citeA{bali2011} & 1962-2005 & -1 & 1 \\
Highest 5 days of return & rmax5\_21d & \citeA{bali2017} & 1993-2012 & -1 & 1 \\
Return volatility & rvol\_21d & \citeA{anghod2006} & 1963-2000 & -1 & 1 \\
Years 6-10 lagged returns, nonannual & seas\_6\_10na & \citeA{heston2008} & 1965-2002 & -1 & 1 \\
Share turnover & turnover\_126d & \citeA{datar1998} & 1963-1991 & -1 & 1 \\
Number of zero trades with turnover as tiebreaker (1 month) & zero\_trades\_21d & \citeA{liu2006} & 1963-2003 & 1 & 0 \\
Number of zero trades with turnover as tiebreaker (6 months) & zero\_trades\_126d & \citeA{liu2006} & 1963-2003 & 1 & 1 \\
Number of zero trades with turnover as tiebreaker (12 months) & zero\_trades\_252d & \citeA{liu2006} & 1963-2003 & 1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Momentum}} \\
Current price to high price over last year & prc\_highprc\_252d & \citeA{george2004} & 1963-2001 & 1 & 1 \\
Residual momentum t-6 to t-1 & resff3\_6\_1 & \citeA{blitz2011} & 1930-2009 & 1 & 1 \\
Residual momentum t-12 to t-1 & resff3\_12\_1 & \citeA{blitz2011} & 1930-2009 & 1 & 1 \\
Price momentum t-3 to t-1 & ret\_3\_1 & \citeA{jegadeesh1993} & 1965-1989 & 1 & 1 \\
Price momentum t-6 to t-1 & ret\_6\_1 & \citeA{jegadeesh1993} & 1965-1989 & 1 & 1 \\
Price momentum t-9 to t-1 & ret\_9\_1 & \citeA{jegadeesh1993} & 1965-1989 & 1 & 1 \\
Price momentum t-12 to t-1 & ret\_12\_1 & \citeA{jegadeesh1993} & 1965-1989 & 1 & 1 \\
Year 1-lagged return, nonannual & seas\_1\_1na & \citeA{heston2008} & 1965-2002 & 1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Profit Growth}} \\
Change sales minus change Inventory & dsale\_dinv & \citeA{abarbanell1998} & 1974-1988 & 1 & 1 \\
Change sales minus change receivables & dsale\_drec & \citeA{abarbanell1998} & 1974-1988 & -1 & 0 \\
Change sales minus change SG\&A & dsale\_dsga & \citeA{abarbanell1998} & 1974-1988 & 1 & 0 \\
Change in quarterly return on assets & niq\_at\_chg1 &   & 1972-2016 & 1 & 0 \\
Change in quarterly return on equity & niq\_be\_chg1 &   & 1967-2016 & 1 & 0 \\
Standardized earnings surprise & niq\_su & \citeA{foster1984} & 1974-1981 & 1 & 1 \\
Change in operating cash flow to assets & ocf\_at\_chg1 & \citeA{bouchaud2019} & 1990-2015 & 1 & 1 \\
Price momentum t-12 to t-7 & ret\_12\_7 & \citeA{novy2012} & 1925-2010 & 1 & 1 \\
Labor force efficiency & sale\_emp\_gr1 & \citeA{abarbanell1998} & 1974-1988 & 1 & 0 \\
Standardized Revenue surprise & saleq\_su & \citeA{jegadeesh2006} & 1987-2003 & 1 & 1 \\
Year 1-lagged return, annual & seas\_1\_1an & \citeA{heston2008} & 1965-2002 & 1 & 1 \\
Tax expense surprise & tax\_gr1a & \citeA{thomas2011} & 1977-2006 & 1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Profitability}} \\
Coefficient of variation for dollar trading volume & dolvol\_var\_126d & \citeA{chordia2001} & 1966-1995 & -1 & 1 \\
Return on net operating assets & ebit\_bev & \citeA{soliman2008} & 1984-2002 & 1 & 1 \\
Profit margin & ebit\_sale & \citeA{soliman2008} & 1984-2002 & 1 & 1 \\
Pitroski F-score & f\_score & \citeA{piotroski2000} & 1976-1996 & 1 & 1 \\
Return on equity & ni\_be & \citeA{haugen1996} & 1979-1993 & 1 & 1 \\
Quarterly return on equity & niq\_be & \citeA{hou2015} & 1972-2012 & 1 & 1 \\
Ohlson O-score & o\_score & \citeA{dichev1998} & 1981-1995 & -1 & 1 \\
Operating cash flow to assets & ocf\_at & \citeA{bouchaud2019} & 1990-2015 & 1 & 1 \\
Operating profits-to-book equity & ope\_be & \citeA{fama2015} & 1963-2013 & 1 & 1 \\
Operating profits-to-lagged book equity & ope\_bel1 &   & 1967-2016 & 1 & 0 \\
Coefficient of variation for share turnover & turnover\_var\_126d & \citeA{chordia2001} & 1966-1995 & -1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Quality}} \\
Capital turnover & at\_turnover & \citeA{haugen1996} & 1979-1993 & 1 & 0 \\
Cash-based operating profits-to-book assets & cop\_at &   & 1967-2016 & 1 & 0 \\
Cash-based operating profits-to-lagged book assets & cop\_atl1 & \citeA{ball2016} & 1963-2014 & 1 & 1 \\
Change gross margin minus change sales & dgp\_dsale & \citeA{abarbanell1998} & 1974-1988 & 1 & 0 \\
Gross profits-to-assets & gp\_at & \citeA{novy2013} & 1963-2010 & 1 & 1 \\
Gross profits-to-lagged assets & gp\_atl1 &   & 1967-2016 & 1 & 0 \\
Mispricing factor: Performance & mispricing\_perf & \citeA{stambaugh2017} & 1967-2013 & 1 & 1 \\
Number of consecutive quarters with earnings increases & ni\_inc8q & \citeA{barth1999} & 1982-1992 & 1 & 0 \\
Quarterly return on assets & niq\_at & \citeA{balakrishnan2010} & 1976-2005 & 1 & 1 \\
Operating profits-to-book assets & op\_at &   & 1963-2013 & 1 & 1 \\
Operating profits-to-lagged book assets & op\_atl1 & \citeA{ball2016} & 1963-2014 & 1 & 1 \\
Operating leverage & opex\_at & \citeA{novy2011} & 1963-2008 & 1 & 1 \\
Quality minus Junk: Composite & qmj & \citeA{asness2019}& 1957-2016 & 1 & 1 \\
Quality minus Junk: Growth & qmj\_growth & \citeA{asness2019}& 1957-2016 & 1 & 1 \\
Quality minus Junk: Profitability & qmj\_prof & \citeA{asness2019} & 1957-2016 & 1 & 1 \\
Quality minus Junk: Safety & qmj\_safety & \citeA{asness2019} & 1957-2016 & 1 & 1 \\
Assets turnover & sale\_bev & \citeA{soliman2008} & 1984-2002 & 1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Seasonality}} \\
Market correlation & corr\_1260d & \citeA{asness2020} & 1925-2015 & -1 & 1 \\
Coskewness & coskew\_21d & \citeA{harvey2000} & 1963-1993 & -1 & 1 \\
Net debt issuance & dbnetis\_at & \citeA{bradshaw2006} & 1971-2000 & -1 & 1 \\
Kaplan-Zingales index & kz\_index & \citeA{lamont2001} & 1968-1995 & 1 & 1 \\
Change in long-term investments & lti\_gr1a & \citeA{richardson2005} & 1962-2001 & -1 & 1 \\
Taxable income-to-book income & pi\_nix & \citeA{lev2004} & 1973-2000 & 1 & 1 \\
Years 2-5 lagged returns, annual & seas\_2\_5an & \citeA{heston2008} & 1965-2002 & 1 & 1 \\
Years 6-10 lagged returns, annual & seas\_6\_10an & \citeA{heston2008} & 1965-2002 & 1 & 1 \\
Years 11-15 lagged returns, annual & seas\_11\_15an & \citeA{heston2008} & 1965-2002 & 1 & 1 \\
Years 11-15 lagged returns, nonannual & seas\_11\_15na & \citeA{heston2008} & 1965-2002 & -1 & 0 \\
Years 16-20 lagged returns, annual & seas\_16\_20an & \citeA{heston2008} & 1965-2002 & -1 & 1 \\
Change in short-term investments & sti\_gr1a & \citeA{richardson2005} & 1962-2001 & 1 & 0 \\
\\
\multicolumn{6}{c}{\underline{\bf Size}} \\
Amihud Measure & ami\_126d & \citeA{amihud2002} & 1964-1997 & 1 & 1 \\
Dollar trading volume & dolvol\_126d & \citeA{brennan1998} & 1966-1995 & -1 & 1 \\
Market Equity & market\_equity & \citeA{banz1981} & 1926-1975 & -1 & 1 \\
Price per share & prc & \citeA{miller1982} & 1940-1978 & -1 & 1 \\
R\&D-to-market & rd\_me & \citeA{chan2001} & 1975-1995 & 1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Short-Term Reversal}} \\
Idiosyncratic skewness from the CAPM & iskew\_capm\_21d &   & 1967-2016 & -1 & 0 \\
Idiosyncratic skewness from the Fama-French 3-factor model & iskew\_ff3\_21d & \citeA{bali2016} & 1925-2021 & -1 & 1 \\
Idiosyncratic skewness from the q-factor model & iskew\_hxz4\_21d &   & 1967-2016 & -1 & 0 \\
Short-term reversal & ret\_1\_0 & \citeA{jegadeesh1990} & 1929-1982 & -1 & 1 \\
Highest 5 days of return scaled by volatility & rmax5\_rvol\_21d & \citeA{asness2020} & 1925-2015 & -1 & 1 \\
Total skewness & rskew\_21d & \citeA{bali2016} & 1925-2021 & -1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Value}} \\
Assets-to-market & at\_me & \citeA{fama1992} & 1963-1990 & 1 & 0 \\
Book-to-market equity & be\_me & \citeA{rosenberg1985} & 1973-1984 & 1 & 1 \\
Book-to-market enterprise value & bev\_mev & \citeA{penman2007} & 1962-2001 & 1 & 1 \\
Net stock issues & chcsho\_12m & \citeA{pontiff2008} & 1970-2003 & -1 & 1 \\
Debt-to-market & debt\_me & \citeA{bhandari1988} & 1948-1979 & 1 & 1 \\
Dividend yield & div12m\_me & \citeA{litzenberger1979} & 1940-1980 & 1 & 1 \\
Ebitda-to-market enterprise value & ebitda\_mev & \citeA{loughran2011} & 1963-2009 & 1 & 1 \\
Equity duration & eq\_dur & \citeA{dechow2004} & 1962-1998 & -1 & 1 \\
Net equity issuance & eqnetis\_at & \citeA{bradshaw2006} & 1971-2000 & -1 & 1 \\
Equity net payout & eqnpo\_12m & \citeA{daniel2006} & 1968-2003 & 1 & 1 \\
Net payout yield & eqnpo\_me & \citeA{boudoukh2007} & 1984-2003 & 1 & 1 \\
Payout yield & eqpo\_me & \citeA{boudoukh2007} & 1984-2003 & 1 & 1 \\
Free cash flow-to-price & fcf\_me & \citeA{lakonishok1994} & 1963-1990 & 1 & 1 \\
Intrinsic value-to-market & ival\_me & \citeA{frankel1998} & 1975-1993 & 1 & 0 \\
Net total issuance & netis\_at & \citeA{bradshaw2006} & 1971-2000 & -1 & 1 \\
Earnings-to-price & ni\_me & \citeA{basu1983} & 1963-1979 & 1 & 1 \\
Operating cash flow-to-market & ocf\_me & \citeA{desai2004} & 1973-1997 & 1 & 1 \\
Sales-to-market & sale\_me & \citeA{barbee1996} & 1979-1991 & 1 & 1 \\
\\
\multicolumn{6}{c}{\underline{\bf Other Factors}} \\
Assets & assets & & & & \\
Sales & sales & & & & \\
Book Equity & book\_equity & & & & \\
Net Income & net\_income & & & & \\
Enterprise Value & enterprise\_value & & & & \\
Current Asset Growth 1yr & ca\_gr1 & & & & \\
Non-Current Asset Growth 1yr & nca\_gr1 & & & & \\
Total Liabilities Growth 1yr & lt\_gr1 & & & & \\
Current Liabilities Growth 1yr & cl\_gr1 & & & & \\
Non-Current Liabilities Growth 1yr & ncl\_gr1 & & & & \\
Book Equity Growth 1yr & be\_gr1 & & & & \\
Preferred Stock Growth 1 yr & pstk\_gr1 & & & & \\
Total Debt Growth 1yr & debt\_gr1 & & & & \\
Cost of Goods Sold Growth 1yr & cogs\_gr1 & & & & \\
Selling, General, and Administrative Expenses Growth 1yr & sga\_gr1 & & & & \\
Operating Expenses Growth 1yr & opex\_gr1 & & & & \\
Asset Growth 3yr & at\_gr3 & & & & \\
Current Asset Growth 3yr & ca\_gr3 & & & & \\
Non-Current Asset Growth 3yr & nca\_gr3 & & & & \\
Total Liabilities Growth 3yr & lt\_gr3 & & & & \\
Current Liabilities Growth 3yr & cl\_gr3 & & & & \\
Non-Current Liabilities Growth 3yr & ncl\_gr3 & & & & \\
Book Equity Growth 3yr & be\_gr3 & & & & \\
Preferred Stock Growth 3yr & pstk\_gr3 & & & & \\
Cost of Goods Sold Growth 3yr & cogs\_gr3 & & & & \\
Selling, General, and Administrative Expenses Growth 3yr & sga\_gr3 & & & & \\
Operating Expenses Growth 3yr & opex\_gr3 & & & & \\
Gross Profit Change 1yr & gp\_gr1a & & & & \\
Operating Cash Flow Change 1yr & ocf\_gr1a & & & & \\
Cash and Short-Term Investments Change 1yr & cash\_gr1a & & & & \\
Receivables Change 1yr & rec\_gr1a & & & & \\
Property, Plans and Equipment Gross Change 1yr & ppeg\_gr1a & & & & \\
Intangible Assets Change 1yr & intan\_gr1a & & & & \\
Short-Term Debt Change 1yr & debtst\_gr1a & & & & \\
Accounts Payable Change 1yr & ap\_gr1a & & & & \\
Income Tax Payable Change 1yr & txp\_gr1a & & & & \\
Long-Term Debt Change 1yr & debtlt\_gr1a & & & & \\
Deferred Taxes and Investment Credit Change 1yr & txditc\_gr1a & & & & \\
Non-Current Operating Liabilities Change 1yr & ncol\_gr1a & & & & \\
Operating Assets Change 1yr & oa\_gr1a & & & & \\
Operating Liabilities Change 1yr & ol\_gr1a & & & & \\
Financial Assets Change 1yr & fna\_gr1a & & & & \\
Operating Profit before Depreciation Change 1yr & ebitda\_gr1a & & & & \\
Operating Profit after Depreciation Change 1yr & ebit\_gr1a & & & & \\
Operating Earnings to Equity Change 1yr & ope\_gr1a & & & & \\
Net Income Change 1yr & ni\_gr1a & & & & \\
Depreciation and Amortization Change 1yr & dp\_gr1a & & & & \\
Free Cash Flow Change 1yr & fcf\_gr1a & & & & \\
Net Working Capital Change 1yr & nwc\_gr1a & & & & \\
Net Income Including Extraordinary Items Change 1yr & nix\_gr1a & & & & \\
Equity Net Issuance Change 1yr & eqnetis\_gr1a & & & & \\
Net Long-Term Debt Issuance Change 1yr & dltnetis\_gr1a & & & & \\
Net Short-Term Debt Issuance Change 1yr & dstnetis\_gr1a & & & & \\
Net Debt Issuance Change 1yr & dbnetis\_gr1a & & & & \\
Net Issuance Change 1yr & netis\_gr1a & & & & \\
Financial Cash Flow Change 1yr & fincf\_gr1a & & & & \\
Equity Net Payout Change 1yr & eqnpo\_gr1a & & & & \\
Dividend Payout Ratio Change 1yr & div\_gr1a & & & & \\
Equity Buyback Change 1yr & eqbb\_gr1a & & & & \\
Equity Issuance Change 1yr & eqis\_gr1a & & & & \\
Net Equity Payout Change 1yr & eqpo\_gr1a & & & & \\
Capital Expenditures Change 1yr & capx\_gr1a & & & & \\
Gross Profit Change 3yr & gp\_gr3a & & & & \\
Operating Cash Flow Change 3yr & ocf\_gr3a & & & & \\
Cash and Short-Term Investments Change 3yr & cash\_gr3a & & & & \\
Inventory Change 3yr & inv\_gr3a & & & & \\
Receivables Change 3yr & rec\_gr3a & & & & \\
Property, Plans and Equipment Gross Change 3yr & ppeg\_gr3a & & & & \\
Investment and Advances Change 3yr & lti\_gr3a & & & & \\
Intangible Assets Change 3yr & intan\_gr3a & & & & \\
Short-Term Debt Change 3yr & debtst\_gr3a & & & & \\
Accounts Payable Change 3yr & ap\_gr3a & & & & \\
Income Tax Payable Change 3yr & txp\_gr3a & & & & \\
Long-Term Debt Change 3yr & debtlt\_gr3a & & & & \\
Deferred Taxes and Investment Credit Change 3yr & txditc\_gr3a & & & & \\
Current Operating Assets Change 3yr & coa\_gr3a & & & & \\
Current Operating Liabilities Change 3yr & col\_gr3a & & & & \\
Current Operating Working Capital Change 3yr & cowc\_gr3a & & & & \\
Non-Current Operating Assets Change 3yr & ncoa\_gr3a & & & & \\
Net Non-Current Operating Assets Change 3yr & nncoa\_gr3a & & & & \\
Operating Assets Change 3yr & oa\_gr3a & & & & \\
Operating Liabilities Change 3yr & ol\_gr3a & & & & \\
Net Operating Assets Change 3yr & noa\_gr3a & & & & \\
Financial Assets Change 3yr & fna\_gr3a & & & & \\
Financial Liabilities Change 3yr & fnl\_gr3a & & & & \\
Net Financial Assets Change 3yr & nfna\_gr3a & & & & \\
Operating Profit before Depreciation Change 3yr & ebitda\_gr3a & & & & \\
Operating Profit after Depreciation Change 3yr & ebit\_gr3a & & & & \\
Operating Earnings to Equity Change 3yr & ope\_gr3a & & & & \\
Net Income Change 3yr & ni\_gr3a & & & & \\
Depreciation and Amortization Change 3yr & dp\_gr3a & & & & \\
Free Cash Flow Change 3yr & fcf\_gr3a & & & & \\
Net Working Capital Change 3yr & nwc\_gr3a & & & & \\
Inventory Change 1yr & inv\_gr3a & & & & \\
Non-Current Operating Liabilities Change 3yr & ncol\_gr3a & & & & \\
Net Income Including Extraordinary Items Change 3yr & nix\_gr3a & & & & \\
Equity Net Issuance Change 3yr & eqnetis\_gr3a & & & & \\
Net Long-Term Debt Issuance Change 3yr & dltnetis\_gr3a & & & & \\
Net Short-Term Debt Issuance Change 3yr & dstnetis\_gr3a & & & & \\
Net Debt Issuance Change 3yr & dbnetis\_gr3a & & & & \\
Net Issuance Change 3yr & netis\_gr3a & & & & \\
Financial Cash Flow Change 3yr & fincf\_gr3a & & & & \\
Net Working Capital Change 3yr & nwc\_gr3a & & & & \\
Equity Net Payout Change 3yr & eqnpo\_gr3a & & & & \\
Effective Tax Rate Change 3yr & tax\_gr3a & & & & \\
Dividend Payout Ratio Change 3yr & div\_gr3a & & & & \\
Equity Buyback Change 3yr & eqbb\_gr3a & & & & \\
Equity Issuance Change 3yr & eqis\_gr3a & & & & \\
Net Equity Payout Change 3yr & eqpo\_gr3a & & & & \\
Capital Expenditures Change 3yr & capx\_gr3a & & & & \\
Capital Expenditures scaled by Assets & capx\_at & & & & \\
R\&D scaled by Assets & rd\_at & & & & \\
Special Items scaled by Assets & spi\_at & & & & \\
Extraordinary Items and Discontinued Operations scaled by Assets & xido\_at & & & & \\
Non-Recurring Items scaled by Assets & nri\_at & & & & \\
Gross Profit Margin & gp\_sale & & & & \\
Operating Profit Margin before Depreciation & ebitda\_sale & & & & \\
Pretax Profit Margin & pi\_sale & & & & \\
Net Profit Margin before extraordinary income & ni\_sale & & & & \\
Net Profit Margin & nix\_sale & & & & \\
Free Cash Flow Margin & fcf\_sale & & & & \\
Operating Cash Flow Margin & ocf\_sale & & & & \\
Operating Profit before Depreciation scaled by Assets & ebitda\_at & & & & \\
Operating Profit after Depreciation scaled by Assets & ebit\_at & & & & \\
Firm Income scaled by Assets & fi\_at & & & & \\
Net Income Including Extraordinary Items scaled by BE & nix\_be & & & & \\
Operating Cash Flow scaled by BE & ocf\_be & & & & \\
Free Cash Flow scaled by BE & fcf\_be & & & & \\
Gross Profit scaled by BEV & gp\_bev & & & & \\
Operating Profit before Depreciation scaled by BEV & ebitda\_bev & & & & \\
Firm Income scaled by BEV & fi\_bev & & & & \\
Cash Based Operating Profitability scaled by BEV & cop\_bev & & & & \\
Gross Profit scaled by PPEN & gp\_ppen & & & & \\
Operating Profit before Depreciation scaled by PPEN & ebitda\_ppen & & & & \\
Free Cash Flow scaled by PPEN & fcf\_ppen & & & & \\
Financial Cash Flow scaled by Assets & fincf\_at & & & & \\
Equity Issuance scaled by Assets & eqis\_at & & & & \\
Net Long-Term Debt Issuance scaled by Assets & dltnetis\_at & & & & \\
Net Short-Term Debt Issuance scaled by Assets & dstnetis\_at & & & & \\
Equity Net Payout scaled by Assets & eqnpo\_at & & & & \\
Net Equity Payout scaled by Assets & eqbb\_at & & & & \\
Total Dividends scaled by Assets & div\_at & & & & \\
Common Equity scaled by BEV & be\_bev & & & & \\
Total Debt scaled by BEV & debt\_bev & & & & \\
Cash and Short-Term Investments scaled by BEV & cash\_bev & & & & \\
Preferred Stock scaled by BEV & pstk\_bev & & & & \\
Long-Term Debt scaled by BEV & debtlt\_bev & & & & \\
Short-Term Debt scaled by BEV & debtst\_bev & & & & \\
Total Debt scaled by MEV & debt\_mev & & & & \\
Preferred Stock scaled by MEV & pstk\_mev & & & & \\
Long-Term Debt scaled by MEV & debtlt\_mev & & & & \\
Short-Term Debt scaled by MEV & debtst\_mev & & & & \\
Interest scaled by Total Debt & int\_debt & & & & \\
Interest scaled by Long-Term Debt & int\_debtlt & & & & \\
Operating Profit before Depreciation scaled by Total Debt & ebitda\_debt & & & & \\
Profit before D\&A scaled by Current Liabilities & profit\_cl & & & & \\
Operating Cash Flow scaled by Current Liabilities & ocf\_cl & & & & \\
Operating Cash Flow scaled by Total Debt & ocf\_debt & & & & \\
Cash Balance scaled by Total Liabilities & cash\_lt & & & & \\
Inventory scaled by Current Assets & inv\_act & & & & \\
Receivables scaled by Current Assets & rec\_act & & & & \\
Short-Term Debt scaled by Total Debt & debtst\_debt & & & & \\
Current Liabilities scaled by Total Liabilities & cl\_lt & & & & \\
Long-Term Debt scaled by Total Debt & debtlt\_debt & & & & \\
Free Cash Flow scaled by Operating Cash Flow & fcf\_ocf & & & & \\
Total Liabilities scaled by Total Tangible Assets & lt\_ppen & & & & \\
Long-Term Debt to Book Equity & debtlt\_be & & & & \\
Working Capital scaled by Assets & nwc\_at & & & & \\
Debt-to-Assets & debt\_at & & & & \\
Debt to Shareholders' Equity Ratio & debt\_be & & & & \\
Interest Coverage Ratio & ebit\_int & & & & \\
Days Inventory Outstanding & inv\_days & & & & \\
Days Sales Outstanding & rec\_days & & & & \\
Days Accounts Payable Outstanding & ap\_days & & & & \\
Cash Conversion Cycle & cash\_conversion & & & & \\
Cash Ratio & cash\_cl & & & & \\
Quick Ratio & caliq\_cl & & & & \\
Current Ratio & ca\_cl & & & & \\
Inventory Turnover & inv\_turnover & & & & \\
Receivables Turnover & rec\_turnover & & & & \\
Account Payables Turnover & ap\_turnover & & & & \\
Advertising scaled by Sales & adv\_sale & & & & \\
Labor Expense scaled by Sales & staff\_sale & & & & \\
Sales scaled by Total Stockholders' Equity & sale\_be & & & & \\
Dividend Payout Ratio & div\_ni & & & & \\
Sales scaled by Working Capital & sale\_nwc & & & & \\
Effective Tax Rate & tax\_pi & & & & \\
Intrinsic Value & intrinsic\_value & & & & \\
Cash and Short-Term Investments scaled by Market Equity & cash\_me & & & & \\
Gross Profit scaled by ME & gp\_me & & & & \\
Operating Profit before Depreciation scaled by ME & ebitda\_me & & & & \\
Operating Profit after Depreciation scaled by ME & ebit\_me & & & & \\
Operating Earnings to Equity scaled by ME & ope\_me & & & & \\
Net Income Including Extraordinary Items scaled by ME & nix\_me & & & & \\
Cash Based Operating Profitability scaled by ME & cop\_me & & & & \\
Book Equity scaled by MEV & be\_mev & & & & \\
Total Assets scaled by MEV & at\_mev & & & & \\
Cash and Short-Term Investments scaled by MEV & cash\_mev & & & & \\
Property, Plans and Equipment Net scaled by MEV & ppen\_mev & & & & \\
Total Dividends scaled by ME & div\_me & & & & \\
Equity Buyback scaled by ME & eqbb\_me & & & & \\
Equity Issuance scaled by ME & eqis\_me & & & & \\
Equity Net Issuance scaled by ME & eqnetis\_me & & & & \\
Net Long-Term Debt Issuance scaled by MEV & & & & \\
Net Short-Term Debt Issuance scaled by MEV & dstnetis\_mev & & & & \\
Net Debt Issuance scaled by MEV & dbnetis\_mev & & & & \\
Net Issuance scaled by MEV & netis\_mev & & & & \\
Gross Profit scaled by MEV & gp\_mev & & & & \\
Operating Profit after Depreciation scaled by MEV & ebit\_mev & & & & \\
Sales scaled by MEV & sale\_mev & & & & \\
Operating Cash Flow scaled by MEV & ocf\_mev & & & & \\
Free Cash Flow scaled by MEV & fcf\_mev & & & & \\
Cash Based Operating Profitability scaled by MEV & cop\_mev & & & & \\
Financial Cash Flow Change scaled by MEV & fincf\_mev & & & & \\
Net Income to Sales Quarterly Volatility & niq\_saleq\_std & & & & \\
Net Income scaled by Employees & ni\_emp & & & & \\
Sales scaled by Employees & sale\_emp & & & & \\
Net Income scaled by Assets & ni\_at & & & & \\
Quarterly ROE Volatility & roeq\_be\_std & & & & \\
ROE Volatility & roe\_be\_std & & & & \\
Gross Product to Assets 5 yr Change & gpoa\_ch5 & & & & \\
ROE 5 yr Change & roe\_ch5 & & & & \\
ROA 5 yr Change & roa\_ch5 & & & & \\
Operating Cash Flow to Assets 5 yr Change & cfoa\_ch5 & & & & \\
Gross Product to Sales 5 yr Change & gmar\_ch5 & & & & \\
Dividend to Price - 1 Month & div1m\_me & & & & \\
Dividend to Price - 3 Months & div3m\_me & & & & \\
Dividend to Price - 6 Months & div6m\_me & & & & \\
Special Dividend to Price - 1 Month & divspc1m\_me & & & \\
Special Dividend to Price - 12 Month & divspc12m\_me & & & & \\
Change in Shares - 1 Month & chcsho\_1m & & & & \\
Change in Shares - 3 Month & chcsho\_3m & & & & \\
Change in Shares - 6 Month & chcsho\_6m & & & & \\
Net Equity Payout - 1 Month & eqnpo\_1m & & & & \\
Net Equity Payout - 3 Month & eqnpo\_3m & & & & \\
Net Equity Payout - 6 Month & eqnpo\_6m & & & & \\
Momentum 0-2 Months & ret\_2\_0 & & & & \\
Momentum 0-3 Months & ret\_3\_0 & & & & \\
Momentum 0-6 Months & ret\_6\_0 & & & & \\
Momentum 0-9 Months & ret\_9\_0 & & & & \\
Momentum 0-12 Months & ret\_12\_0 & & & & \\
Momentum 1-18 Months & ret\_18\_1 & & & & \\
Momentum 1-24 Months & ret\_24\_1 & & & & \\
Momentum 12-24 Months & ret\_24\_12 & & & & \\
Momentum 1-36 Months & ret\_36\_1 & & & & \\
Momentum 12-36 Months & ret\_36\_12 & & & & \\
Momentum 1-48 Months & ret\_48\_1 & & & & \\
Momentum 12-48 Months & ret\_48\_12 & & & & \\
Momentum 1-60 Months & ret\_60\_1 & & & & \\
Momentum 36-60 Months & ret\_60\_36 & & & & \\
Market beta (21 days) & beta\_21d & & & & \\
Market beta (252 days) & beta\_252d & & & & \\
Return volatility (252 days) & rvol\_252d & & & & \\
Idiosyncratic volatility from the CAPM (60 months) & ivol\_capm\_60m
& & & & \\
The high-low return volatility & rvolhl\_21d & \citeA{corwin2012} & & \\
        \hline 
        \hline \\[-8ex]
    \label{tab:clusters:factors}
\end{longtable}

\hspace{-1cm}
\begin{minipage}{1.05\textwidth}
        \footnotesize
        {\it Note:} This table shows cluster names as underlined section headings and, for each cluster, a description of the factors included, the variable name used in the code, the original reference, the sample period used in the original reference, the sign of the factor (``1'' means ``long'', ``-1'' means ``short''), and whether the original reference found the factor to be significant (``1'' means ``yes'', ``0'' means ``no''). For example, the first value factor ``at\_me'' goes long stocks with high values of assets-to-market and shorts those with low values (and would be done the reverse if the sign was ``-1'' instead of ``1'').
\end{minipage}

\newpage
\section{Miscellaneous}

{\scriptsize
	\begin{longtable}{@{\extracolsep{\fill}}|m{6.5cm}|l|m{6.5cm}|@{}}
	\caption{Country Code Key and MSCI Categorization \label{country_classification}}\\

	\hline
	Country & EXCNTRY-Country Code & MSCI Categorization \\
	\hline
	\endfirsthead

	\hline
	Country & EXCNTRY-Country Code & MSCI Categorization \\
	\hline
	\endhead

	\hline
	\endfoot

	\hline\hline
	\endlastfoot

	Argentina & ARG & standalone \\[1ex]
	Australia & AUS & developed \\[1ex]
	Austria & AUT & developed \\[1ex]
	Bahrain & BHR & frontier \\[1ex]
	Bangladesh & BGD & frontier \\[1ex]
	Belgium & BEL & developed \\[1ex]
	Bermuda & BMU & not rated \\[1ex]
	Botswana & BWA & standalone \\[1ex]
	Brazil & BRA & emerging \\[1ex]
	Bulgaria & BGR & standalone \\[1ex]
	Canada & CAN & developed \\[1ex]
	Chile & CHL & emerging \\[1ex]
	China & CHN & emerging \\[1ex]
	Colombia & COL & emerging \\[1ex]
	Croatia & HRV & frontier \\[1ex]
	Cyprus & CYP & not rated \\[1ex]
	Czech Republic & CZE & emerging \\[1ex]
	Denmark & DNK & developed \\[1ex]
	Ecuador & ECU & not rated \\[1ex]
	Egypt & EGY & emerging \\[1ex]
	Estonia & EST & frontier \\[1ex]
	Finland & FIN & developed \\[1ex]
	France & FRA & developed \\[1ex]
	Germany & DEU & developed \\[1ex]
	Ghana & GHA & not rated \\[1ex]
	Greece & GRC & emerging \\[1ex]
	Guernsey & GGY & not rated \\[1ex]
	Hong Kong & HKG & developed \\[1ex]
	Hungary & HUN & emerging \\[1ex]
	Iceland & ISL & frontier \\[1ex]
	India & IND & emerging \\[1ex]
	Indonesia & IDN & emerging \\[1ex]
	Iran, Islamic Republic of & IRN & not rated \\[1ex]
	Ireland & IRL & developed \\[1ex]
	Israel & ISR & developed \\[1ex]
	Italy & ITA & developed \\[1ex]
	Jamaica & JAM & standalone \\[1ex]
	Japan & JPN & developed \\[1ex]
	Jordan & JOR & frontier \\[1ex]
	Kazakhstan & KAZ & frontier \\[1ex]
	Kenya & KEN & frontier \\[1ex]
	Korea, Republic of & KOR & emerging \\[1ex]
	Kuwait & KWT & emerging \\[1ex]
	Latvia & LVA & frontier \\[1ex]
	Lebanon & LBN & standalone \\[1ex]
	Lithuania & LTU & frontier \\[1ex]
	Luxembourg & LUX & not rated \\[1ex]
	Malawi & MWI & not rated \\[1ex]
	Malaysia & MYS & emerging \\[1ex]
	Malta & MLT & standalone \\[1ex]
	Mauritius & MUS & frontier \\[1ex]
	Mexico & MEX & emerging \\[1ex]
	Morocco & MAR & frontier \\[1ex]
	Namibia & NAM & not rated \\[1ex]
	Netherlands & NLD & developed \\[1ex]
	New Zealand & NZL & developed \\[1ex]
	Nigeria & NGA & standalone \\[1ex]
	Norway & NOR & developed \\[1ex]
	Oman & OMN & frontier \\[1ex]
	Pakistan & PAK & frontier \\[1ex]
	Palestinian Territory, Occupied & PSE & standalone \\[1ex]
	Peru & PER & emerging \\[1ex]
	Philippines & PHL & emerging \\[1ex]
	Poland & POL & emerging \\[1ex]
	Portugal & PRT & developed \\[1ex]
	Qatar & QAT & emerging \\[1ex]
	Romania & ROU & frontier \\[1ex]
	Russian Federation & RUS & not rated \\[1ex]
	Saudi Arabia & SAU & emerging \\[1ex]
	Senegal & SEN & frontier \\[1ex]
	Serbia & SRB & frontier \\[1ex]
	Singapore & SGP & developed \\[1ex]
	Slovakia & SVK & not rated \\[1ex]
	Slovenia & SVN & frontier \\[1ex]
	South Africa & ZAF & emerging \\[1ex]
	Spain & ESP & developed \\[1ex]
	Sri Lanka & LKA & frontier \\[1ex]
	Sweden & SWE & developed \\[1ex]
	Switzerland & CHE & developed \\[1ex]
	Taiwan, Province of China & TWN & emerging \\[1ex]
	Tanzania, United Republic of & TZA & not rated \\[1ex]
	Thailand & THA & emerging \\[1ex]
	Trinidad and Tobago & TTO & standalone \\[1ex]
	Tunisia & TUN & frontier \\[1ex]
	Turkey & TUR & emerging \\[1ex]
	Uganda & UGA & not rated \\[1ex]
	Ukraine & UKR & standalone \\[1ex]
	United Arab Emirates & ARE & emerging \\[1ex]
	United Kingdom & GBR & developed \\[1ex]
	United States & USA & developed \\[1ex]
	Uruguay & URY & not rated \\[1ex]
	Venezuela, Bolivarian Republic of & VEN & not rated \\[1ex]
	Viet Nam & VNM & frontier \\[1ex]
	Zambia & ZMB & not rated \\[1ex]
	Zimbabwe & ZWE & standalone \\
\end{longtable}
}


% ... (end section)

%\end{section}

\bibliographystyle{apacite}
\bibliography{documentation.bib}

\end{document}
